#Garmin Data
#WGSP01
```{r WGSP01,echo=FALSE}
WGSP01_S2HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP01//Session2//Parvo//GARMIN_S2.CSV")
WGSP01_S3HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP01//Session3//Parvo//GARMIN_S3.CSV")
WGSP01_S4HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP01//Session4//Parvo//GARMIN_S4.CSV")
```
##SESSION 2
```{r, echo=FALSE}
WGSP01_S2HR <- WGSP01_S2HR%>%
  mutate(session = 2)%>%
  mutate(participant = "P1")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 6.7)%>%
  mutate(type = "FW")
WGSP01_S2HR$session <- as.factor(WGSP01_S2HR$session)
WGSP01_S2HR$secs <- as_hms(WGSP01_S2HR$secs)
WGSP01_S2HR = subset(WGSP01_S2HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP01_S2HR$secs <- as.character(WGSP01_S2HR$secs)
WGSP01_S2HR$secs <- gsub(":", ".", WGSP01_S2HR$secs, perl=TRUE)
WGSP01_S2HR$secs <- stri_sub(WGSP01_S2HR$secs,4)
WGSP01_S2HR$secs <- as.numeric(WGSP01_S2HR$secs)

WGSP01_S2HR <- WGSP01_S2HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>6.09 & secs<9.09, "WARM_UP",
                     ifelse(secs>9.51 & secs<29.51, "EXERCISE", "BLANK"))))

```

##SESSION 3
```{r, echo=FALSE}
WGSP01_S3HR <- WGSP01_S3HR%>%
  mutate(session = 3)%>%
  mutate(participant = "P1")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 88)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 5.2)%>%
  mutate(type = "SWBFR")  
WGSP01_S3HR$session <- as.factor(WGSP01_S3HR$session)
WGSP01_S3HR$secs <- as_hms(WGSP01_S3HR$secs)
WGSP01_S3HR = subset(WGSP01_S3HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP01_S3HR$secs <- as.character(WGSP01_S3HR$secs)
WGSP01_S3HR$secs <- gsub(":", ".", WGSP01_S3HR$secs, perl=TRUE)
WGSP01_S3HR$secs <- stri_sub(WGSP01_S3HR$secs,4)
WGSP01_S3HR$secs <- as.numeric(WGSP01_S3HR$secs)

WGSP01_S3HR <- WGSP01_S3HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.34 & secs<8.34, "WARM_UP",
                     ifelse(secs>12.09 & secs<32.09, "EXERCISE", "BLANK"))))
```

##SESSION 4
```{r, echo=FALSE}
WGSP01_S4HR <- WGSP01_S4HR%>%
  mutate(session = 4)%>%
  mutate(participant = "P1")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 5.2)%>%
  mutate(type = "SW")
WGSP01_S4HR$session <- as.factor(WGSP01_S4HR$session)
WGSP01_S4HR$secs <- as_hms(WGSP01_S4HR$secs)
WGSP01_S4HR = subset(WGSP01_S4HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP01_S4HR$secs <- as.character(WGSP01_S4HR$secs)
WGSP01_S4HR$secs <- gsub(":", ".", WGSP01_S4HR$secs, perl=TRUE)
WGSP01_S4HR$secs <- stri_sub(WGSP01_S4HR$secs,4)
WGSP01_S4HR$secs <- as.numeric(WGSP01_S4HR$secs)

WGSP01_S4HR <- WGSP01_S4HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.33 & secs<8.33, "WARM_UP",
                     ifelse(secs>8.59 & secs<28.59, "EXERCISE", "BLANK"))))
```

```{r, P1 Bind, echo=FALSE}
WGSP01_HR <- rbind(WGSP01_S2HR,WGSP01_S3HR,WGSP01_S4HR)%>%
  mutate(age = 26)%>%
  mutate(sex = "male")%>%
  mutate(HRMAX = (211-(0.64*age)))%>%
  mutate(PerHRMAX = ((hr/HRMAX)*100))

```

#WGSP02
```{r, echo=FALSE}
WGSP02_S1HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP02//Session1//Parvo//GARMIN_S1.CSV")
WGSP02_S2HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP02//Session2//Parvo//GARMIN_S2.CSV")
WGSP02_S3HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP02//Session3//Parvo//GARMIN_S3.CSV")
WGSP02_S4HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP02//Session4//Parvo//GARMIN_S4.CSV")
```

##SESSION 1
```{r, echo=FALSE}
WGSP02_S1HR <- WGSP02_S1HR%>%
  mutate(session = 1)%>%
  mutate(participant = "P2")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 101)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 5.5)%>%
  mutate(type = "SWBFR")
WGSP02_S1HR$session <- as.factor(WGSP02_S1HR$session)
WGSP02_S1HR$secs <- as_hms(WGSP02_S1HR$secs)
WGSP02_S1HR = subset(WGSP02_S1HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP02_S1HR$secs <- as.character(WGSP02_S1HR$secs)
WGSP02_S1HR$secs <- gsub(":", ".", WGSP02_S1HR$secs, perl=TRUE)
WGSP02_S1HR$secs <- stri_sub(WGSP02_S1HR$secs,4)
WGSP02_S1HR$secs <- as.numeric(WGSP02_S1HR$secs)

WGSP02_S1HR <- WGSP02_S1HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>6.14 & secs<9.14, "WARM_UP",
                     ifelse(secs>12.27 & secs<32.27, "EXERCISE", "BLANK"))))
```

##SESSION 2
```{r, echo=FALSE}
WGSP02_S2HR <- WGSP02_S2HR%>%
  mutate(session = 2)%>%
  mutate(participant = "P2")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 5.5)%>%
  mutate(type = "SW")
WGSP02_S2HR$session <- as.factor(WGSP02_S2HR$session)
WGSP02_S2HR$secs <- as_hms(WGSP02_S2HR$secs)
WGSP02_S2HR = subset(WGSP02_S2HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP02_S2HR$secs <- as.character(WGSP02_S2HR$secs)
WGSP02_S2HR$secs <- gsub(":", ".", WGSP02_S2HR$secs, perl=TRUE)
WGSP02_S2HR$secs <- stri_sub(WGSP02_S2HR$secs,4)
WGSP02_S2HR$secs <- as.numeric(WGSP02_S2HR$secs)

WGSP02_S2HR <- WGSP02_S2HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.29 & secs<8.29, "WARM_UP",
                     ifelse(secs>8.56 & secs<28.56, "EXERCISE", "BLANK"))))

```

##SESSION 3
```{r, echo=FALSE}
WGSP02_S3HR <- WGSP02_S3HR%>%
  mutate(session = 3)%>%
  mutate(participant = "P2")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 101)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 7.1)%>%
  mutate(type = "FWBFR")
WGSP02_S3HR$session <- as.factor(WGSP02_S3HR$session)
WGSP02_S3HR$secs <- as_hms(WGSP02_S3HR$secs)
WGSP02_S3HR = subset(WGSP02_S3HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP02_S3HR$secs <- as.character(WGSP02_S3HR$secs)
WGSP02_S3HR$secs <- gsub(":", ".", WGSP02_S3HR$secs, perl=TRUE)
WGSP02_S3HR$secs <- stri_sub(WGSP02_S3HR$secs,4)
WGSP02_S3HR$secs <- as.numeric(WGSP02_S3HR$secs)

WGSP02_S3HR <- WGSP02_S3HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>6.13 & secs<9.13, "WARM_UP",
                     ifelse(secs>11.56 & secs<31.56, "EXERCISE", "BLANK"))))

```

##SESSION 4
```{r, echo=FALSE}
WGSP02_S4HR <- WGSP02_S4HR%>%
  mutate(session = 4)%>%
  mutate(participant = "P2")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 7.1)%>%
  mutate(type = "FW")  
WGSP02_S4HR$session <- as.factor(WGSP02_S4HR$session)
WGSP02_S4HR$secs <- as_hms(WGSP02_S4HR$secs)
WGSP02_S4HR = subset(WGSP02_S4HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP02_S4HR$secs <- as.character(WGSP02_S4HR$secs)
WGSP02_S4HR$secs <- gsub(":", ".", WGSP02_S4HR$secs, perl=TRUE)
WGSP02_S4HR$secs <- stri_sub(WGSP02_S4HR$secs,4)
WGSP02_S4HR$secs <- as.numeric(WGSP02_S4HR$secs)

WGSP02_S4HR <- WGSP02_S4HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.28 & secs<8.28, "WARM_UP",
                     ifelse(secs>8.53 & secs<28.53, "EXERCISE", "BLANK"))))

```

```{r, echo=FALSE}
WGSP02_HR <- rbind(WGSP02_S1HR, WGSP02_S2HR,WGSP02_S3HR,WGSP02_S4HR)%>%
  mutate(age = 25)%>%
  mutate(sex = "male")%>%
  mutate(HRMAX = (211-(0.64*age)))%>%
  mutate(PerHRMAX = ((hr/HRMAX)*100))

```

#WGSP03
```{r}
WGSP03_S1HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP03//Session1//Parvo//GARMIN_S1.CSV")
WGSP03_S2HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP03//Session2//Parvo//GARMIN_S2.CSV")
WGSP03_S3HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP03//Session3//Parvo//GARMIN_S3.CSV")
WGSP03_S4HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP03//Session4//Parvo//GARMIN_S4.CSV")
```

##SESSION 1
```{r}
WGSP03_S1HR <- WGSP03_S1HR%>%
  mutate(session = 1)%>%
  mutate(participant = "P3")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 90)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 5.7)%>%
  mutate(type = "FWBFR")
WGSP03_S1HR$session <- as.factor(WGSP03_S1HR$session)
WGSP03_S1HR$secs <- as_hms(WGSP03_S1HR$secs)
WGSP03_S1HR = subset(WGSP03_S1HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP03_S1HR$secs <- as.character(WGSP03_S1HR$secs)
WGSP03_S1HR$secs <- gsub(":", ".", WGSP03_S1HR$secs, perl=TRUE)
WGSP03_S1HR$secs <- stri_sub(WGSP03_S1HR$secs,4)
WGSP03_S1HR$secs <- as.numeric(WGSP03_S1HR$secs)

WGSP03_S1HR <- WGSP03_S1HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.46 & secs<8.46, "WARM_UP",
                     ifelse(secs>12.49 & secs<32.49, "EXERCISE", "BLANK"))))

```

##SESSION 2
```{r}
WGSP03_S2HR <- WGSP03_S2HR%>%
  mutate(session = 2)%>%
  mutate(participant = "P3")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 5.7)%>%
  mutate(type = "FW")
WGSP03_S2HR$session <- as.factor(WGSP03_S2HR$session)
WGSP03_S2HR$secs <- as_hms(WGSP03_S2HR$secs)
WGSP03_S2HR = subset(WGSP03_S2HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP03_S2HR$secs <- as.character(WGSP03_S2HR$secs)
WGSP03_S2HR$secs <- gsub(":", ".", WGSP03_S2HR$secs, perl=TRUE)
WGSP03_S2HR$secs <- stri_sub(WGSP03_S2HR$secs,4)
WGSP03_S2HR$secs <- as.numeric(WGSP03_S2HR$secs)

WGSP03_S2HR <- WGSP03_S2HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.35 & secs<8.35, "WARM_UP",
                     ifelse(secs>9.06 & secs<29.06, "EXERCISE", "BLANK"))))

```

##SESSION 3
```{r}
WGSP03_S3HR <- WGSP03_S3HR%>%
  mutate(session = 3)%>%
  mutate(participant = "P3")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 90)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 4.4)%>%
mutate(type = "SWBFR")
WGSP03_S3HR$session <- as.factor(WGSP03_S3HR$session)
WGSP03_S3HR$secs <- as_hms(WGSP03_S3HR$secs)
WGSP03_S3HR = subset(WGSP03_S3HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP03_S3HR$secs <- as.character(WGSP03_S3HR$secs)
WGSP03_S3HR$secs <- gsub(":", ".", WGSP03_S3HR$secs, perl=TRUE)
WGSP03_S3HR$secs <- stri_sub(WGSP03_S3HR$secs,4)
WGSP03_S3HR$secs <- as.numeric(WGSP03_S3HR$secs)

WGSP03_S3HR <- WGSP03_S3HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.34& secs<8.34, "WARM_UP",
                     ifelse(secs>12.03 & secs<32.03, "EXERCISE", "BLANK"))))

```

##SESSION 4
```{r}
WGSP03_S4HR <- WGSP03_S4HR%>%
  mutate(session = 4)%>%
  mutate(participant = "P3")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 4.4)%>%
  mutate(type = "SW")
WGSP03_S4HR$session <- as.factor(WGSP03_S4HR$session)
WGSP03_S4HR$secs <- as_hms(WGSP03_S4HR$secs)
WGSP03_S4HR = subset(WGSP03_S4HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP03_S4HR$secs <- as.character(WGSP03_S4HR$secs)
WGSP03_S4HR$secs <- gsub(":", ".", WGSP03_S4HR$secs, perl=TRUE)
WGSP03_S4HR$secs <- stri_sub(WGSP03_S4HR$secs,4)
WGSP03_S4HR$secs <- as.numeric(WGSP03_S4HR$secs)

WGSP03_S4HR <- WGSP03_S4HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.30 & secs<8.30, "WARM_UP",
                     ifelse(secs>8.50 & secs<28.50, "EXERCISE", "BLANK"))))

```

```{r}
WGSP03_HR <- rbind(WGSP03_S1HR, WGSP03_S2HR,WGSP03_S3HR,WGSP03_S4HR)%>%
  mutate(age = 37)%>%
  mutate(sex = "female")%>%
  mutate(HRMAX = (211-(0.64*age)))%>%
  mutate(PerHRMAX = ((hr/HRMAX)*100))


```


#WGSP04
```{r}
WGSP04_S2HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP04//Session2//Parvo//GARMIN_S2.CSV")
WGSP04_S3HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP04//Session3//Parvo//GARMIN_S3.CSV")
WGSP04_S4HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP04//Session4//Parvo//GARMIN_S4.CSV")
```
##SESSION 2
```{r}
WGSP04_S2HR <- WGSP04_S2HR%>%
  mutate(session = 2)%>%
  mutate(participant = "P4")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 5.3)%>%
  mutate(type = "SW")
WGSP04_S2HR$session <- as.factor(WGSP04_S2HR$session)
WGSP04_S2HR$secs <- as_hms(WGSP04_S2HR$secs)
WGSP04_S2HR = subset(WGSP04_S2HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP04_S2HR$secs <- as.character(WGSP04_S2HR$secs)
WGSP04_S2HR$secs <- gsub(":", ".", WGSP04_S2HR$secs, perl=TRUE)
WGSP04_S2HR$secs <- stri_sub(WGSP04_S2HR$secs,4)
WGSP04_S2HR$secs <- as.numeric(WGSP04_S2HR$secs)

WGSP04_S2HR <- WGSP04_S2HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>6.10 & secs<9.10, "WARM_UP",
                     ifelse(secs>9.49 & secs<27.49, "EXERCISE", "BLANK"))))
```

##SESSION 3
```{r}
WGSP04_S3HR <- WGSP04_S3HR%>%
  mutate(session = 3)%>%
  mutate(participant = "P4")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 102)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 6.8)%>%
  mutate(type = "FWBFR")
WGSP04_S3HR$session <- as.factor(WGSP04_S3HR$session)
WGSP04_S3HR$secs <- as_hms(WGSP04_S3HR$secs)
WGSP04_S3HR = subset(WGSP04_S3HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP04_S3HR$secs <- as.character(WGSP04_S3HR$secs)
WGSP04_S3HR$secs <- gsub(":", ".", WGSP04_S3HR$secs, perl=TRUE)
WGSP04_S3HR$secs <- stri_sub(WGSP04_S3HR$secs,4)
WGSP04_S3HR$secs <- as.numeric(WGSP04_S3HR$secs)

WGSP04_S3HR <- WGSP04_S3HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.34 & secs<8.34, "WARM_UP",
                     ifelse(secs>13.02 & secs<15.02, "EXERCISE", "BLANK"))))

```

##SESSION 4
```{r}
WGSP04_S4HR <- WGSP04_S4HR%>%
  mutate(session = 4)%>%
  mutate(participant = "P4")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 6.8)%>%
  mutate(type = "FW")
WGSP04_S4HR$session <- as.factor(WGSP04_S4HR$session)
WGSP04_S4HR$secs <- as_hms(WGSP04_S4HR$secs)
WGSP04_S4HR = subset(WGSP04_S4HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP04_S4HR$secs <- as.character(WGSP04_S4HR$secs)
WGSP04_S4HR$secs <- gsub(":", ".", WGSP04_S4HR$secs, perl=TRUE)
WGSP04_S4HR$secs <- stri_sub(WGSP04_S4HR$secs,4)
WGSP04_S4HR$secs <- as.numeric(WGSP04_S4HR$secs)

WGSP04_S4HR <- WGSP04_S4HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.42 & secs<8.42, "WARM_UP",
                     ifelse(secs>9.14 & secs<11.14, "EXERCISE", "BLANK"))))

```

```{r}
WGSP04_HR <- rbind(WGSP04_S2HR,WGSP04_S3HR,WGSP04_S4HR)%>%
  mutate(age = 29)%>%
  mutate(sex = "female")%>%
  mutate(HRMAX = (211-(0.64*age)))%>%
  mutate(PerHRMAX = ((hr/HRMAX)*100))
```

#WGSP06
```{r}
WGSP06_S2HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP06//Session2//Parvo//GARMIN_S2.CSV")
WGSP06_S3HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP06//Session3//Parvo//GARMIN_S3.CSV")
WGSP06_S4HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP06//Session4//Parvo//GARMIN_S4.CSV")
```


##SESSION 2
```{r}
WGSP06_S2HR <- WGSP06_S2HR%>%
  mutate(session = 2)%>%
  mutate(participant = "P6")%>%
   mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 5.3)%>%
mutate(type = "SW")
WGSP06_S2HR$session <- as.factor(WGSP06_S2HR$session)
WGSP06_S2HR$secs <- as_hms(WGSP06_S2HR$secs)
WGSP06_S2HR = subset(WGSP06_S2HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP06_S2HR$secs <- as.character(WGSP06_S2HR$secs)
WGSP06_S2HR$secs <- gsub(":", ".", WGSP06_S2HR$secs, perl=TRUE)
WGSP06_S2HR$secs <- stri_sub(WGSP06_S2HR$secs,4)
WGSP06_S2HR$secs <- as.numeric(WGSP06_S2HR$secs)

WGSP06_S2HR <- WGSP06_S2HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>8.10 & secs<11.10, "WARM_UP",
                     ifelse(secs>11.33 & secs<31.33, "EXERCISE", "BLANK"))))

```

##SESSION 3
```{r}
WGSP06_S3HR <- WGSP06_S3HR%>%
  mutate(session = 3)%>%
  mutate(participant = "P6")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 115)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 6.8)%>%
  mutate(type = "FWBFR")
WGSP06_S3HR$session <- as.factor(WGSP06_S3HR$session)
WGSP06_S3HR$secs <- as_hms(WGSP06_S3HR$secs)
WGSP06_S3HR = subset(WGSP06_S3HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP06_S3HR$secs <- as.character(WGSP06_S3HR$secs)
WGSP06_S3HR$secs <- gsub(":", ".", WGSP06_S3HR$secs, perl=TRUE)
WGSP06_S3HR$secs <- stri_sub(WGSP06_S3HR$secs,4)
WGSP06_S3HR$secs <- as.numeric(WGSP06_S3HR$secs)

WGSP06_S3HR <- WGSP06_S3HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.50 & secs<8.50, "WARM_UP",
                     ifelse(secs>13.04 & secs<33.04, "EXERCISE", "BLANK"))))
```

##SESSION 4
```{r}
WGSP06_S4HR <- WGSP06_S4HR%>%
  mutate(session = 4)%>%
  mutate(participant = "P6")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 6.8)%>%
  mutate(type = "FW")
WGSP06_S4HR$session <- as.factor(WGSP06_S4HR$session)
WGSP06_S4HR$secs <- as_hms(WGSP06_S4HR$secs)
WGSP06_S4HR = subset(WGSP06_S4HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP06_S4HR$secs <- as.character(WGSP06_S4HR$secs)
WGSP06_S4HR$secs <- gsub(":", ".", WGSP06_S4HR$secs, perl=TRUE)
WGSP06_S4HR$secs <- stri_sub(WGSP06_S4HR$secs,4)
WGSP06_S4HR$secs <- as.numeric(WGSP06_S4HR$secs)

WGSP06_S4HR <- WGSP06_S4HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.56 & secs<8.56, "WARM_UP",
                     ifelse(secs>9.46 & secs<29.46, "EXERCISE", "BLANK"))))

```

```{r}
WGSP06_HR <- rbind(WGSP06_S2HR,WGSP06_S3HR,WGSP06_S4HR)%>%
  mutate(age = 30)%>%
  mutate(sex = "male")%>%
  mutate(HRMAX = (211-(0.64*age)))%>%
  mutate(PerHRMAX = ((hr/HRMAX)*100))
```

#WGSP07
```{r}
WGSP07_S1HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP07//Session1//Parvo//GARMIN_S1.CSV")
WGSP07_S2HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP07//Session2//Parvo//GARMIN_S2.CSV")
WGSP07_S3HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP07//Session3//Parvo//GARMIN_S3.CSV")
WGSP07_S4HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP07//Session4//Parvo//GARMIN_S4.CSV")
```

##SESSION 1
```{r}
WGSP07_S1HR <- WGSP07_S1HR%>%
  mutate(session = 1)%>%
  mutate(participant = "P7")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 102)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 4.9)%>%
  mutate(type = "SWBFR")
WGSP07_S1HR$session <- as.factor(WGSP07_S1HR$session)
WGSP07_S1HR$secs <- as_hms(WGSP07_S1HR$secs)
WGSP07_S1HR = subset(WGSP07_S1HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP07_S1HR$secs <- as.character(WGSP07_S1HR$secs)
WGSP07_S1HR$secs <- gsub(":", ".", WGSP07_S1HR$secs, perl=TRUE)
WGSP07_S1HR$secs <- stri_sub(WGSP07_S1HR$secs,4)
WGSP07_S1HR$secs <- as.numeric(WGSP07_S1HR$secs)

WGSP07_S1HR <- WGSP07_S1HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>6.23 & secs<9.23, "WARM_UP",
                     ifelse(secs>12.50 & secs<32.50, "EXERCISE", "BLANK"))))

```

##SESSION 2
```{r}
WGSP07_S2HR <- WGSP07_S2HR%>%
  mutate(session = 2)%>%
  mutate(participant = "P7")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 4.9)%>%
  mutate(type = "SW")
WGSP07_S2HR$session <- as.factor(WGSP07_S2HR$session)
WGSP07_S2HR$secs <- as_hms(WGSP07_S2HR$secs)
WGSP07_S2HR = subset(WGSP07_S2HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP07_S2HR$secs <- as.character(WGSP07_S2HR$secs)
WGSP07_S2HR$secs <- gsub(":", ".", WGSP07_S2HR$secs, perl=TRUE)
WGSP07_S2HR$secs <- stri_sub(WGSP07_S2HR$secs,4)
WGSP07_S2HR$secs <- as.numeric(WGSP07_S2HR$secs)

WGSP07_S2HR <- WGSP07_S2HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.30 & secs<8.30, "WARM_UP",
                     ifelse(secs>9.10 & secs<29.10, "EXERCISE", "BLANK"))))

```

##SESSION 3
```{r}
WGSP07_S3HR <- WGSP07_S3HR%>%
  mutate(session = 3)%>%
  mutate(participant = "P7")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 102)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 6.3)%>%
  mutate(type = "FWBFR")  
WGSP07_S3HR$session <- as.factor(WGSP07_S3HR$session)
WGSP07_S3HR$secs <- as_hms(WGSP07_S3HR$secs)
WGSP07_S3HR = subset(WGSP07_S3HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP07_S3HR$secs <- as.character(WGSP07_S3HR$secs)
WGSP07_S3HR$secs <- gsub(":", ".", WGSP07_S3HR$secs, perl=TRUE)
WGSP07_S3HR$secs <- stri_sub(WGSP07_S3HR$secs,4)
WGSP07_S3HR$secs <- as.numeric(WGSP07_S3HR$secs)

WGSP07_S3HR <- WGSP07_S3HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.47 & secs<8.47, "WARM_UP",
                     ifelse(secs>11.39 & secs<31.39, "EXERCISE", "BLANK"))))

```

##SESSION 4
```{r}
WGSP07_S4HR <- WGSP07_S4HR%>%
  mutate(session = 4)%>%
  mutate(participant = "P7")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 6.3)%>%
  mutate(type = "FW")  
WGSP07_S4HR$session <- as.factor(WGSP07_S4HR$session)
WGSP07_S4HR$secs <- as_hms(WGSP07_S4HR$secs)
WGSP07_S4HR = subset(WGSP07_S4HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP07_S4HR$secs <- as.character(WGSP07_S4HR$secs)
WGSP07_S4HR$secs <- gsub(":", ".", WGSP07_S4HR$secs, perl=TRUE)
WGSP07_S4HR$secs <- stri_sub(WGSP07_S4HR$secs,4)
WGSP07_S4HR$secs <- as.numeric(WGSP07_S4HR$secs)

WGSP07_S4HR <- WGSP07_S4HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.50 & secs<8.50, "WARM_UP",
                     ifelse(secs>9.22 & secs<29.22, "EXERCISE", "BLANK"))))

```

```{r}
WGSP07_HR <- rbind(WGSP07_S1HR, WGSP07_S2HR,WGSP07_S3HR,WGSP07_S4HR)%>%
  mutate(age = 23)%>%
  mutate(sex = "male")%>%
  mutate(HRMAX = (211-(0.64*age)))%>%
  mutate(PerHRMAX = ((hr/HRMAX)*100))
```

#WGSP08
```{r}
WGSP08_S1HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP08//Session1//Parvo//GARMIN_S1.CSV")
WGSP08_S2HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP08//Session2//Parvo//GARMIN_S2.CSV")
WGSP08_S3HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP08//Session3//Parvo//GARMIN_S3.CSV")
WGSP08_S4HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP08//Session4//Parvo//GARMIN_S4.CSV")
```

##SESSION 1
```{r}
WGSP08_S1HR <- WGSP08_S1HR%>%
  mutate(session = 1)%>%
  mutate(participant = "P8")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 116)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 5.2)%>%
  mutate(type = "SWBFR")
WGSP08_S1HR$session <- as.factor(WGSP08_S1HR$session)
WGSP08_S1HR$secs <- as_hms(WGSP08_S1HR$secs)
WGSP08_S1HR = subset(WGSP08_S1HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP08_S1HR$secs <- as.character(WGSP08_S1HR$secs)
WGSP08_S1HR$secs <- gsub(":", ".", WGSP08_S1HR$secs, perl=TRUE)
WGSP08_S1HR$secs <- stri_sub(WGSP08_S1HR$secs,4)
WGSP08_S1HR$secs <- as.numeric(WGSP08_S1HR$secs)

WGSP08_S1HR <- WGSP08_S1HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>13.38 & secs<16.38, "WARM_UP",
                     ifelse(secs>19.47 & secs<39.47, "EXERCISE", "BLANK"))))

```

##SESSION 2
```{r}
WGSP08_S2HR <- WGSP08_S2HR%>%
  mutate(session = 2)%>%
  mutate(participant = "P8")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 5.2)%>%
  mutate(type = "SW")
WGSP08_S2HR$session <- as.factor(WGSP08_S2HR$session)
WGSP08_S2HR$secs <- as_hms(WGSP08_S2HR$secs)
WGSP08_S2HR = subset(WGSP08_S2HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP08_S2HR$secs <- as.character(WGSP08_S2HR$secs)
WGSP08_S2HR$secs <- gsub(":", ".", WGSP08_S2HR$secs, perl=TRUE)
WGSP08_S2HR$secs <- stri_sub(WGSP08_S2HR$secs,4)
WGSP08_S2HR$secs <- as.numeric(WGSP08_S2HR$secs)

WGSP08_S2HR <- WGSP08_S2HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.35 & secs<8.35, "WARM_UP",
                     ifelse(secs>9.04 & secs<29.04, "EXERCISE", "BLANK"))))

```

##SESSION 3
```{r}
WGSP08_S3HR <- WGSP08_S3HR%>%
  mutate(session = 3)%>%
  mutate(participant = "P8")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 116)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 6.7)%>%
  mutate(type = "FWBFR")
WGSP08_S3HR$session <- as.factor(WGSP08_S3HR$session)
WGSP08_S3HR$secs <- as_hms(WGSP08_S3HR$secs)
WGSP08_S3HR = subset(WGSP08_S3HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP08_S3HR$secs <- as.character(WGSP08_S3HR$secs)
WGSP08_S3HR$secs <- gsub(":", ".", WGSP08_S3HR$secs, perl=TRUE)
WGSP08_S3HR$secs <- stri_sub(WGSP08_S3HR$secs,4)
WGSP08_S3HR$secs <- as.numeric(WGSP08_S3HR$secs)

WGSP08_S3HR <- WGSP08_S3HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.28 & secs<8.28, "WARM_UP",
                     ifelse(secs>12.24 & secs<17.24, "EXERCISE", "BLANK"))))

```

##SESSION 4
```{r}
WGSP08_S4HR <- WGSP08_S4HR%>%
  mutate(session = 4)%>%
  mutate(participant = "P8")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 6.7)%>%
  mutate(type = "FW")
WGSP08_S4HR$session <- as.factor(WGSP08_S4HR$session)
WGSP08_S4HR$secs <- as_hms(WGSP08_S4HR$secs)
WGSP08_S4HR = subset(WGSP08_S4HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP08_S4HR$secs <- as.character(WGSP08_S4HR$secs)
WGSP08_S4HR$secs <- gsub(":", ".", WGSP08_S4HR$secs, perl=TRUE)
WGSP08_S4HR$secs <- stri_sub(WGSP08_S4HR$secs,4)
WGSP08_S4HR$secs <- as.numeric(WGSP08_S4HR$secs)

WGSP08_S4HR <- WGSP08_S4HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.33 & secs<8.33, "WARM_UP",
                     ifelse(secs>8.59 & secs<13.59, "EXERCISE", "BLANK"))))

```

```{r}
WGSP08_HR <- rbind(WGSP08_S1HR, WGSP08_S2HR,WGSP08_S3HR,WGSP08_S4HR)%>%
  mutate(age = 22)%>%
  mutate(sex = "female")%>%
  mutate(HRMAX = (211-(0.64*age)))%>%
  mutate(PerHRMAX = ((hr/HRMAX)*100))
```


#WGSP09
```{r}
WGSP09_S1HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP09//Session1//Parvo//GARMIN_S1.CSV")
WGSP09_S2HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP09//Session2//Parvo//GARMIN_S2.CSV")
WGSP09_S3HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP09//Session3//Parvo//GARMIN_S3.CSV")
WGSP09_S4HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP09//Session4//Parvo//GARMIN_S4.CSV")
```

##SESSION 1
```{r}
WGSP09_S1HR <- WGSP09_S1HR%>%
  mutate(session = 1)%>%
  mutate(participant = "P9")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 108)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 7.0)%>%
  mutate(type = "FWBFR")
WGSP09_S1HR$session <- as.factor(WGSP09_S1HR$session)
WGSP09_S1HR$secs <- as_hms(WGSP09_S1HR$secs)
WGSP09_S1HR = subset(WGSP09_S1HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP09_S1HR$secs <- as.character(WGSP09_S1HR$secs)
WGSP09_S1HR$secs <- gsub(":", ".", WGSP09_S1HR$secs, perl=TRUE)
WGSP09_S1HR$secs <- stri_sub(WGSP09_S1HR$secs,4)
WGSP09_S1HR$secs <- as.numeric(WGSP09_S1HR$secs)

WGSP09_S1HR <- WGSP09_S1HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>6.05 & secs<9.05, "WARM_UP",
                     ifelse(secs>12.16 & secs<18.08, "EXERCISE", "BLANK"))))

```

##SESSION 2
```{r}
WGSP09_S2HR <- WGSP09_S2HR%>%
  mutate(session = 2)%>%
  mutate(participant = "P9")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 7.0)%>%
  mutate(type = "FW")
WGSP09_S2HR$session <- as.factor(WGSP09_S2HR$session)
WGSP09_S2HR$secs <- as_hms(WGSP09_S2HR$secs)
WGSP09_S2HR = subset(WGSP09_S2HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP09_S2HR$secs <- as.character(WGSP09_S2HR$secs)
WGSP09_S2HR$secs <- gsub(":", ".", WGSP09_S2HR$secs, perl=TRUE)
WGSP09_S2HR$secs <- stri_sub(WGSP09_S2HR$secs,4)
WGSP09_S2HR$secs <- as.numeric(WGSP09_S2HR$secs)

WGSP09_S2HR <- WGSP09_S2HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.30 & secs<8.30, "WARM_UP",
                     ifelse(secs>8.56 & secs<14.56, "EXERCISE", "BLANK"))))


```

##SESSION 3
```{r}
WGSP09_S3HR <- WGSP09_S3HR%>%
  mutate(session = 3)%>%
  mutate(participant = "P9")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 108)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 5.5)%>%
mutate(type = "SWBFR")
WGSP09_S3HR$session <- as.factor(WGSP09_S3HR$session)
WGSP09_S3HR$secs <- as_hms(WGSP09_S3HR$secs)
WGSP09_S3HR = subset(WGSP09_S3HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP09_S3HR$secs <- as.character(WGSP09_S3HR$secs)
WGSP09_S3HR$secs <- gsub(":", ".", WGSP09_S3HR$secs, perl=TRUE)
WGSP09_S3HR$secs <- stri_sub(WGSP09_S3HR$secs,4)
WGSP09_S3HR$secs <- as.numeric(WGSP09_S3HR$secs)

WGSP09_S3HR <- WGSP09_S3HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.34 & secs<8.34, "WARM_UP",
                     ifelse(secs>11.43 & secs<31.43, "EXERCISE", "BLANK"))))


```

##SESSION 4
```{r}
WGSP09_S4HR <- WGSP09_S4HR%>%
  mutate(session = 4)%>%
  mutate(participant = "P9")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 5.5)%>%
  mutate(type = "SW")
WGSP09_S4HR$session <- as.factor(WGSP09_S4HR$session)
WGSP09_S4HR$secs <- as_hms(WGSP09_S4HR$secs)
WGSP09_S4HR = subset(WGSP09_S4HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP09_S4HR$secs <- as.character(WGSP09_S4HR$secs)
WGSP09_S4HR$secs <- gsub(":", ".", WGSP09_S4HR$secs, perl=TRUE)
WGSP09_S4HR$secs <- stri_sub(WGSP09_S4HR$secs,4)
WGSP09_S4HR$secs <- as.numeric(WGSP09_S4HR$secs)

WGSP09_S4HR <- WGSP09_S4HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.30 & secs<8.30, "WARM_UP",
                     ifelse(secs>9.08 & secs<29.08, "EXERCISE", "BLANK"))))


```

```{r}
WGSP09_HR <- rbind(WGSP09_S1HR, WGSP09_S2HR,WGSP09_S3HR,WGSP09_S4HR)%>%
  mutate(age = 29)%>%
  mutate(sex = "male")%>%
  mutate(HRMAX = (211-(0.64*age)))%>%
  mutate(PerHRMAX = ((hr/HRMAX)*100))
```

#WGSP10
```{r}
WGSP10_S1HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP10//Session1//Parvo//GARMIN_S1.CSV")
WGSP10_S2HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP10//Session2//Parvo//GARMIN_S2.CSV")
WGSP10_S3HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP10//Session3//Parvo//GARMIN_S3.CSV")
WGSP10_S4HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP10//Session4//Parvo//GARMIN_S4.CSV")
```

##SESSION 1
```{r}
WGSP10_S1HR <- WGSP10_S1HR%>%
  mutate(session = 1)%>%
  mutate(participant = "P10")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 185)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 5.3)%>%
  mutate(type = "SWBFR")
WGSP10_S1HR$session <- as.factor(WGSP10_S1HR$session)
WGSP10_S1HR$secs <- as_hms(WGSP10_S1HR$secs)
WGSP10_S1HR = subset(WGSP10_S1HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP10_S1HR$secs <- as.character(WGSP10_S1HR$secs)
WGSP10_S1HR$secs <- gsub(":", ".", WGSP10_S1HR$secs, perl=TRUE)
WGSP10_S1HR$secs <- stri_sub(WGSP10_S1HR$secs,4)
WGSP10_S1HR$secs <- as.numeric(WGSP10_S1HR$secs)

WGSP10_S1HR <- WGSP10_S1HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.41 & secs<8.41, "WARM_UP",
                     ifelse(secs>11.28 & secs<31.28, "EXERCISE", "BLANK"))))

```

##SESSION 2
```{r}
WGSP10_S2HR <- WGSP10_S2HR%>%
  mutate(session = 2)%>%
  mutate(participant = "P10")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 5.3)%>%
  mutate(type = "SW")
WGSP10_S2HR$session <- as.factor(WGSP10_S2HR$session)
WGSP10_S2HR$secs <- as_hms(WGSP10_S2HR$secs)
WGSP10_S2HR = subset(WGSP10_S2HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP10_S2HR$secs <- as.character(WGSP10_S2HR$secs)
WGSP10_S2HR$secs <- gsub(":", ".", WGSP10_S2HR$secs, perl=TRUE)
WGSP10_S2HR$secs <- stri_sub(WGSP10_S2HR$secs,4)
WGSP10_S2HR$secs <- as.numeric(WGSP10_S2HR$secs)

WGSP10_S2HR <- WGSP10_S2HR%>%
  mutate(INTERVALS = ifelse(secs>0.10 & secs<5.10,"PRE_REST",
                     ifelse(secs>6.41 & secs<9.41, "WARM_UP",
                     ifelse(secs>10.17 & secs<30.17, "EXERCISE", "BLANK"))))


```

##SESSION 3
```{r}
WGSP10_S3HR <- WGSP10_S3HR%>%
  mutate(session = 3)%>%
  mutate(participant = "P10")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 85)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 6.8)%>%
mutate(type = "FWBFR")
WGSP10_S3HR$session <- as.factor(WGSP10_S3HR$session)
WGSP10_S3HR$secs <- as_hms(WGSP10_S3HR$secs)
WGSP10_S3HR = subset(WGSP10_S3HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP10_S3HR$secs <- as.character(WGSP10_S3HR$secs)
WGSP10_S3HR$secs <- gsub(":", ".", WGSP10_S3HR$secs, perl=TRUE)
WGSP10_S3HR$secs <- stri_sub(WGSP10_S3HR$secs,4)
WGSP10_S3HR$secs <- as.numeric(WGSP10_S3HR$secs)

WGSP10_S3HR <- WGSP10_S3HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.28 & secs<8.28, "WARM_UP",
                     ifelse(secs>11.20 & secs<31.20, "EXERCISE", "BLANK"))))


```

##SESSION 4
```{r}
WGSP10_S4HR <- WGSP10_S4HR%>%
  mutate(session = 4)%>%
  mutate(participant = "P10")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 6.8)%>%
  mutate(type = "FW")
WGSP10_S4HR$session <- as.factor(WGSP10_S4HR$session)
WGSP10_S4HR$secs <- as_hms(WGSP10_S4HR$secs)
WGSP10_S4HR = subset(WGSP10_S4HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP10_S4HR$secs <- as.character(WGSP10_S4HR$secs)
WGSP10_S4HR$secs <- gsub(":", ".", WGSP10_S4HR$secs, perl=TRUE)
WGSP10_S4HR$secs <- stri_sub(WGSP10_S4HR$secs,4)
WGSP10_S4HR$secs <- as.numeric(WGSP10_S4HR$secs)

WGSP10_S4HR <- WGSP10_S4HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.37 & secs<8.37, "WARM_UP",
                     ifelse(secs>9.03 & secs<29.03, "EXERCISE", "BLANK"))))


```

```{r}
WGSP10_HR <- rbind(WGSP10_S1HR, WGSP10_S2HR,WGSP10_S3HR,WGSP10_S4HR)%>%
  mutate(age = 28)%>%
  mutate(sex = "male")%>%
  mutate(HRMAX = (211-(0.64*age)))%>%
  mutate(PerHRMAX = ((hr/HRMAX)*100))
```

#WGSP11
```{r}
WGSP11_S1HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP11//Session1//Parvo//GARMIN_S1.CSV")
WGSP11_S2HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP11//Session2//Parvo//GARMIN_S2.CSV")
WGSP11_S3HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP11//Session3//Parvo//GARMIN_S3.CSV")
WGSP11_S4HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP11//Session4//Parvo//GARMIN_S4.CSV")
```

##SESSION 1
```{r}
WGSP11_S1HR <- WGSP11_S1HR%>%
  mutate(session = 1)%>%
  mutate(participant = "P11")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 94)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 4.6)%>%
  mutate(type = "SWBFR")
WGSP11_S1HR$session <- as.factor(WGSP11_S1HR$session)
WGSP11_S1HR$secs <- as_hms(WGSP11_S1HR$secs)
WGSP11_S1HR = subset(WGSP11_S1HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP11_S1HR$secs <- as.character(WGSP11_S1HR$secs)
WGSP11_S1HR$secs <- gsub(":", ".", WGSP11_S1HR$secs, perl=TRUE)
WGSP11_S1HR$secs <- stri_sub(WGSP11_S1HR$secs,4)
WGSP11_S1HR$secs <- as.numeric(WGSP11_S1HR$secs)

WGSP11_S1HR <- WGSP11_S1HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.33 & secs<8.33, "WARM_UP",
                     ifelse(secs>11.24 & secs<20.24, "EXERCISE", "BLANK"))))

```

##SESSION 2
```{r}
WGSP11_S2HR <- WGSP11_S2HR%>%
  mutate(session = 2)%>%
  mutate(participant = "P11")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 94)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 5.9)%>%
  mutate(type = "FWBFR")
WGSP11_S2HR$session <- as.factor(WGSP11_S2HR$session)
WGSP11_S2HR$secs <- as_hms(WGSP11_S2HR$secs)
WGSP11_S2HR = subset(WGSP11_S2HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP11_S2HR$secs <- as.character(WGSP11_S2HR$secs)
WGSP11_S2HR$secs <- gsub(":", ".", WGSP11_S2HR$secs, perl=TRUE)
WGSP11_S2HR$secs <- stri_sub(WGSP11_S2HR$secs,4)
WGSP11_S2HR$secs <- as.numeric(WGSP11_S2HR$secs)

WGSP11_S2HR <- WGSP11_S2HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.45 & secs<8.45, "WARM_UP",
                     ifelse(secs>12.01 & secs<19.08, "EXERCISE", "BLANK"))))

```

##SESSION 3
```{r}
WGSP11_S3HR <- WGSP11_S3HR%>%
  mutate(session = 3)%>%
  mutate(participant = "P11")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 4.6)%>%
  mutate(type = "SW")
WGSP11_S3HR$session <- as.factor(WGSP11_S3HR$session)
WGSP11_S3HR$secs <- as_hms(WGSP11_S3HR$secs)
WGSP11_S3HR = subset(WGSP11_S3HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP11_S3HR$secs <- as.character(WGSP11_S3HR$secs)
WGSP11_S3HR$secs <- gsub(":", ".", WGSP11_S3HR$secs, perl=TRUE)
WGSP11_S3HR$secs <- stri_sub(WGSP11_S3HR$secs,4)
WGSP11_S3HR$secs <- as.numeric(WGSP11_S3HR$secs)

WGSP11_S3HR <- WGSP11_S3HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.35 & secs<8.35, "WARM_UP",
                     ifelse(secs>9.00 & secs<18.00, "EXERCISE", "BLANK"))))

```

##SESSION 4
```{r}
WGSP11_S4HR <- WGSP11_S4HR%>%
  mutate(session = 4)%>%
  mutate(participant = "P11")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 5.9)%>%
  mutate(type = "FW")
WGSP11_S4HR$session <- as.factor(WGSP11_S4HR$session)
WGSP11_S4HR$secs <- as_hms(WGSP11_S4HR$secs)
WGSP11_S4HR = subset(WGSP11_S4HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP11_S4HR$secs <- as.character(WGSP11_S4HR$secs)
WGSP11_S4HR$secs <- gsub(":", ".", WGSP11_S4HR$secs, perl=TRUE)
WGSP11_S4HR$secs <- stri_sub(WGSP11_S4HR$secs,4)
WGSP11_S4HR$secs <- as.numeric(WGSP11_S4HR$secs)

WGSP11_S4HR <- WGSP11_S4HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.30 & secs<8.30, "WARM_UP",
                     ifelse(secs>9.19 & secs<16.19, "EXERCISE", "BLANK"))))

```

```{r}
WGSP11_HR <- rbind(WGSP11_S1HR, WGSP11_S2HR,WGSP11_S3HR,WGSP11_S4HR)%>%
  mutate(age = 31)%>%
  mutate(sex = "male")%>%
  mutate(HRMAX = (211-(0.64*age)))%>%
  mutate(PerHRMAX = ((hr/HRMAX)*100))
```

#WGSP012
```{r}
WGSP12_S1HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP12//Session1//Parvo//GARMIN_S1.CSV")
WGSP12_S2HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP12//Session2//Parvo//GARMIN_S2.CSV")
WGSP12_S3HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP12//Session3//Parvo//GARMIN_S3.CSV")
WGSP12_S4HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP12//Session4//Parvo//GARMIN_S4.CSV")
```

##SESSION 1
```{r}
WGSP12_S1HR <- WGSP12_S1HR%>%
  mutate(session = 1)%>%
  mutate(participant = "P12")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 104)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 6.1)%>%
  mutate(type = "FWBFR")
WGSP12_S1HR$session <- as.factor(WGSP12_S1HR$session)
WGSP12_S1HR$secs <- as_hms(WGSP12_S1HR$secs)
WGSP12_S1HR = subset(WGSP12_S1HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP12_S1HR$secs <- as.character(WGSP12_S1HR$secs)
WGSP12_S1HR$secs <- gsub(":", ".", WGSP12_S1HR$secs, perl=TRUE)
WGSP12_S1HR$secs <- stri_sub(WGSP12_S1HR$secs,4)
WGSP12_S1HR$secs <- as.numeric(WGSP12_S1HR$secs)

WGSP12_S1HR <- WGSP12_S1HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>6.04 & secs<9.04, "WARM_UP",
                     ifelse(secs>13.32 & secs<33.32, "EXERCISE", "BLANK"))))

```

##SESSION 2
```{r}
WGSP12_S2HR <- WGSP12_S2HR%>%
  mutate(session = 2)%>%
  mutate(participant = "P12")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 6.1)%>%
  mutate(type = "FW")
WGSP12_S2HR$session <- as.factor(WGSP12_S2HR$session)
WGSP12_S2HR$secs <- as_hms(WGSP12_S2HR$secs)
WGSP12_S2HR = subset(WGSP12_S2HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP12_S2HR$secs <- as.character(WGSP12_S2HR$secs)
WGSP12_S2HR$secs <- gsub(":", ".", WGSP12_S2HR$secs, perl=TRUE)
WGSP12_S2HR$secs <- stri_sub(WGSP12_S2HR$secs,4)
WGSP12_S2HR$secs <- as.numeric(WGSP12_S2HR$secs)

WGSP12_S2HR <- WGSP12_S2HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.35 & secs<8.35, "WARM_UP",
                     ifelse(secs>9.01 & secs<29.01, "EXERCISE", "BLANK"))))

```

##SESSION 3
```{r}
WGSP12_S3HR <- WGSP12_S3HR%>%
  mutate(session = 3)%>%
  mutate(participant = "P12")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 104)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 4.8)%>%
  mutate(type = "SWBFR")
WGSP12_S3HR$session <- as.factor(WGSP12_S3HR$session)
WGSP12_S3HR$secs <- as_hms(WGSP12_S3HR$secs)
WGSP12_S3HR = subset(WGSP12_S3HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP12_S3HR$secs <- as.character(WGSP12_S3HR$secs)
WGSP12_S3HR$secs <- gsub(":", ".", WGSP12_S3HR$secs, perl=TRUE)
WGSP12_S3HR$secs <- stri_sub(WGSP12_S3HR$secs,4)
WGSP12_S3HR$secs <- as.numeric(WGSP12_S3HR$secs)

WGSP12_S3HR <- WGSP12_S3HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.44 & secs<8.44, "WARM_UP",
                     ifelse(secs>11.25 & secs<19.25, "EXERCISE", "BLANK"))))

```

##SESSION 4
```{r}
WGSP12_S4HR <- WGSP12_S4HR%>%
  mutate(session = 4)%>%
  mutate(participant = "P12")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 4.8)%>%
  mutate(type = "SW")
WGSP12_S4HR$session <- as.factor(WGSP12_S4HR$session)
WGSP12_S4HR$secs <- as_hms(WGSP12_S4HR$secs)
WGSP12_S4HR = subset(WGSP12_S4HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP12_S4HR$secs <- as.character(WGSP12_S4HR$secs)
WGSP12_S4HR$secs <- gsub(":", ".", WGSP12_S4HR$secs, perl=TRUE)
WGSP12_S4HR$secs <- stri_sub(WGSP12_S4HR$secs,4)
WGSP12_S4HR$secs <- as.numeric(WGSP12_S4HR$secs)

WGSP12_S4HR <- WGSP12_S4HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.34 & secs<8.34, "WARM_UP",
                     ifelse(secs>8.55 & secs<16.55, "EXERCISE", "BLANK"))))

```

```{r}
WGSP12_HR <- rbind(WGSP12_S1HR, WGSP12_S2HR,WGSP12_S3HR,WGSP12_S4HR)%>%
   mutate(age = 23)%>%
  mutate(sex = "male")%>%
  mutate(HRMAX = (211-(0.64*age)))%>%
  mutate(PerHRMAX = ((hr/HRMAX)*100))
```

#WGSP013
```{r}
WGSP13_S1HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP13//Session1//Parvo//GARMIN_S1.CSV")
WGSP13_S2HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP13//Session2//Parvo//GARMIN_S2.CSV")
WGSP13_S3HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP13//Session3//Parvo//GARMIN_S3.CSV")
WGSP13_S4HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP13//Session4//Parvo//GARMIN_S4.CSV")
```

##SESSION 1
```{r}
WGSP13_S1HR <- WGSP13_S1HR%>%
  mutate(session = 1)%>%
  mutate(participant = "P13")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 96)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 5.1)%>%
  mutate(type = "SWBFR")
WGSP13_S1HR$session <- as.factor(WGSP13_S1HR$session)
WGSP13_S1HR$secs <- as_hms(WGSP13_S1HR$secs)
WGSP13_S1HR = subset(WGSP13_S1HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP13_S1HR$secs <- as.character(WGSP13_S1HR$secs)
WGSP13_S1HR$secs <- gsub(":", ".", WGSP13_S1HR$secs, perl=TRUE)
WGSP13_S1HR$secs <- stri_sub(WGSP13_S1HR$secs,4)
WGSP13_S1HR$secs <- as.numeric(WGSP13_S1HR$secs)

WGSP13_S1HR <- WGSP13_S1HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.33 & secs<8.33, "WARM_UP",
                     ifelse(secs>11.33 & secs<31.33, "EXERCISE", "BLANK"))))

```

##SESSION 2
```{r}
WGSP13_S2HR <- WGSP13_S2HR%>%
  mutate(session = 2)%>%
  mutate(participant = "P13")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 5.1)%>%
  mutate(type = "SW")
WGSP13_S2HR$session <- as.factor(WGSP13_S2HR$session)
WGSP13_S2HR$secs <- as_hms(WGSP13_S2HR$secs)
WGSP13_S2HR = subset(WGSP13_S2HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP13_S2HR$secs <- as.character(WGSP13_S2HR$secs)
WGSP13_S2HR$secs <- gsub(":", ".", WGSP13_S2HR$secs, perl=TRUE)
WGSP13_S2HR$secs <- stri_sub(WGSP13_S2HR$secs,4)
WGSP13_S2HR$secs <- as.numeric(WGSP13_S2HR$secs)

WGSP13_S2HR <- WGSP13_S2HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.34 & secs<8.34, "WARM_UP",
                     ifelse(secs>8.56 & secs<28.56, "EXERCISE", "BLANK"))))

```

##SESSION 3
```{r}
WGSP13_S3HR <- WGSP13_S3HR%>%
  mutate(session = 3)%>%
  mutate(participant = "P13")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 96)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 6.6)%>%
  mutate(type = "FWBFR")
WGSP13_S3HR$session <- as.factor(WGSP13_S3HR$session)
WGSP13_S3HR$secs <- as_hms(WGSP13_S3HR$secs)
WGSP13_S3HR = subset(WGSP13_S3HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP13_S3HR$secs <- as.character(WGSP13_S3HR$secs)
WGSP13_S3HR$secs <- gsub(":", ".", WGSP13_S3HR$secs, perl=TRUE)
WGSP13_S3HR$secs <- stri_sub(WGSP13_S3HR$secs,4)
WGSP13_S3HR$secs <- as.numeric(WGSP13_S3HR$secs)

WGSP13_S3HR <- WGSP13_S3HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.25 & secs<8.25, "WARM_UP",
                     ifelse(secs>11.30 & secs<31.30, "EXERCISE", "BLANK"))))

```

##SESSION 4
```{r}
WGSP13_S4HR <- WGSP13_S4HR%>%
  mutate(session = 4)%>%
  mutate(participant = "P13")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 6.6)%>%
  mutate(type = "FW")
WGSP13_S4HR$session <- as.factor(WGSP13_S4HR$session)
WGSP13_S4HR$secs <- as_hms(WGSP13_S4HR$secs)
WGSP13_S4HR = subset(WGSP13_S4HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP13_S4HR$secs <- as.character(WGSP13_S4HR$secs)
WGSP13_S4HR$secs <- gsub(":", ".", WGSP13_S4HR$secs, perl=TRUE)
WGSP13_S4HR$secs <- stri_sub(WGSP13_S4HR$secs,4)
WGSP13_S4HR$secs <- as.numeric(WGSP13_S4HR$secs)

WGSP13_S4HR <- WGSP13_S4HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.42 & secs<8.42, "WARM_UP",
                     ifelse(secs>9.53 & secs<29.53, "EXERCISE", "BLANK"))))

```

```{r}
WGSP13_HR <- rbind(WGSP13_S1HR, WGSP13_S2HR,WGSP13_S3HR,WGSP13_S4HR)%>%
   mutate(age = 32)%>%
  mutate(sex = "male")%>%
  mutate(HRMAX = (211-(0.64*age)))%>%
  mutate(PerHRMAX = ((hr/HRMAX)*100))
```

#WGSP015
```{r}
WGSP15_S1HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP15//Session1//Parvo//GARMIN_S1.CSV")
WGSP15_S2HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP15//Session2//Parvo//GARMIN_S2.CSV")
WGSP15_S3HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP15//Session3//Parvo//GARMIN_S3.CSV")
WGSP15_S4HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP15//Session4//Parvo//GARMIN_S4.CSV")
```

##SESSION 1
```{r}
WGSP15_S1HR <- WGSP15_S1HR%>%
  mutate(session = 1)%>%
  mutate(participant = "P15")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 114)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 6.3)%>%
  mutate(type = "FWBFR")
WGSP15_S1HR$session <- as.factor(WGSP15_S1HR$session)
WGSP15_S1HR$secs <- as_hms(WGSP15_S1HR$secs)
WGSP15_S1HR = subset(WGSP15_S1HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP15_S1HR$secs <- as.character(WGSP15_S1HR$secs)
WGSP15_S1HR$secs <- gsub(":", ".", WGSP15_S1HR$secs, perl=TRUE)
WGSP15_S1HR$secs <- stri_sub(WGSP15_S1HR$secs,4)
WGSP15_S1HR$secs <- as.numeric(WGSP15_S1HR$secs)

WGSP15_S1HR <- WGSP15_S1HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.32 & secs<8.32, "WARM_UP",
                     ifelse(secs>11.37 & secs<24.37, "EXERCISE", "BLANK"))))

```

##SESSION 2
```{r}
WGSP15_S2HR <- WGSP15_S2HR%>%
  mutate(session = 2)%>%
  mutate(participant = "P15")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 6.3)%>%
  mutate(type = "FW")
WGSP15_S2HR$session <- as.factor(WGSP15_S2HR$session)
WGSP15_S2HR$secs <- as_hms(WGSP15_S2HR$secs)
WGSP15_S2HR = subset(WGSP15_S2HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP15_S2HR$secs <- as.character(WGSP15_S2HR$secs)
WGSP15_S2HR$secs <- gsub(":", ".", WGSP15_S2HR$secs, perl=TRUE)
WGSP15_S2HR$secs <- stri_sub(WGSP15_S2HR$secs,4)
WGSP15_S2HR$secs <- as.numeric(WGSP15_S2HR$secs)

WGSP15_S2HR <- WGSP15_S2HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.32 & secs<8.32, "WARM_UP",
                     ifelse(secs>8.59 & secs<21.59, "EXERCISE", "BLANK"))))

```

##SESSION 3
```{r}
WGSP15_S3HR <- WGSP15_S3HR%>%
  mutate(session = 3)%>%
  mutate(participant = "P15")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 114)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 4.9)%>%
  mutate(type = "SWBFR")
WGSP15_S3HR$session <- as.factor(WGSP15_S3HR$session)
WGSP15_S3HR$secs <- as_hms(WGSP15_S3HR$secs)
WGSP15_S3HR = subset(WGSP15_S3HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP15_S3HR$secs <- as.character(WGSP15_S3HR$secs)
WGSP15_S3HR$secs <- gsub(":", ".", WGSP15_S3HR$secs, perl=TRUE)
WGSP15_S3HR$secs <- stri_sub(WGSP15_S3HR$secs,4)
WGSP15_S3HR$secs <- as.numeric(WGSP15_S3HR$secs)

WGSP15_S3HR <- WGSP15_S3HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.27 & secs<8.27, "WARM_UP",
                     ifelse(secs>11.00 & secs<31.00, "EXERCISE", "BLANK"))))

```

##SESSION 4
```{r}
WGSP15_S4HR <- WGSP15_S4HR%>%
  mutate(session = 4)%>%
  mutate(participant = "P15")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 4.9)%>%
  mutate(type = "SW")
WGSP15_S4HR$session <- as.factor(WGSP15_S4HR$session)
WGSP15_S4HR$secs <- as_hms(WGSP15_S4HR$secs)
WGSP15_S4HR = subset(WGSP15_S4HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP15_S4HR$secs <- as.character(WGSP15_S4HR$secs)
WGSP15_S4HR$secs <- gsub(":", ".", WGSP15_S4HR$secs, perl=TRUE)
WGSP15_S4HR$secs <- stri_sub(WGSP15_S4HR$secs,4)
WGSP15_S4HR$secs <- as.numeric(WGSP15_S4HR$secs)

WGSP15_S4HR <- WGSP15_S4HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.54 & secs<8.54, "WARM_UP",
                     ifelse(secs>9.38 & secs<29.38, "EXERCISE", "BLANK"))))

```

```{r}
WGSP15_HR <- rbind(WGSP15_S1HR, WGSP15_S2HR,WGSP15_S3HR,WGSP15_S4HR)%>%
   mutate(age = 28)%>%
  mutate(sex = "male")%>%
  mutate(HRMAX = (211-(0.64*age)))%>%
  mutate(PerHRMAX = ((hr/HRMAX)*100))
```

#WGSP017
```{r}
WGSP17_S1HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP17//Session1//Parvo//GARMIN_S1.CSV")
WGSP17_S2HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP17//Session2//Parvo//GARMIN_S2.CSV")
WGSP17_S3HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP17//Session3//Parvo//GARMIN_S3.CSV")
WGSP17_S4HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP17//Session4//Parvo//GARMIN_S4.CSV")
```

##SESSION 1
```{r}
WGSP17_S1HR <- WGSP17_S1HR%>%
  mutate(session = 1)%>%
  mutate(participant = "P17")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 100)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 6.5)%>%
  mutate(type = "FWBFR")
WGSP17_S1HR$session <- as.factor(WGSP17_S1HR$session)
WGSP17_S1HR$secs <- as_hms(WGSP17_S1HR$secs)
WGSP17_S1HR = subset(WGSP17_S1HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP17_S1HR$secs <- as.character(WGSP17_S1HR$secs)
WGSP17_S1HR$secs <- gsub(":", ".", WGSP17_S1HR$secs, perl=TRUE)
WGSP17_S1HR$secs <- stri_sub(WGSP17_S1HR$secs,4)
WGSP17_S1HR$secs <- as.numeric(WGSP17_S1HR$secs)

WGSP17_S1HR <- WGSP17_S1HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.28 & secs<8.28, "WARM_UP",
                     ifelse(secs>11.25 & secs<31.25, "EXERCISE", "BLANK"))))

```

##SESSION 2
```{r}
WGSP17_S2HR <- WGSP17_S2HR%>%
  mutate(session = 2)%>%
  mutate(participant = "P17")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 6.5)%>%
  mutate(type = "FW")
WGSP17_S2HR$session <- as.factor(WGSP17_S2HR$session)
WGSP17_S2HR$secs <- as_hms(WGSP17_S2HR$secs)
WGSP17_S2HR = subset(WGSP17_S2HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP17_S2HR$secs <- as.character(WGSP17_S2HR$secs)
WGSP17_S2HR$secs <- gsub(":", ".", WGSP17_S2HR$secs, perl=TRUE)
WGSP17_S2HR$secs <- stri_sub(WGSP17_S2HR$secs,4)
WGSP17_S2HR$secs <- as.numeric(WGSP17_S2HR$secs)

WGSP17_S2HR <- WGSP17_S2HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.30 & secs<8.30, "WARM_UP",
                     ifelse(secs>8.57 & secs<28.57, "EXERCISE", "BLANK"))))

```

##SESSION 3
```{r}
WGSP17_S3HR <- WGSP17_S3HR%>%
  mutate(session = 3)%>%
  mutate(participant = "P17")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 100)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 5.0)%>%
  mutate(type = "SWBFR")
WGSP17_S3HR$session <- as.factor(WGSP17_S3HR$session)
WGSP17_S3HR$secs <- as_hms(WGSP17_S3HR$secs)
WGSP17_S3HR = subset(WGSP17_S3HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP17_S3HR$secs <- as.character(WGSP17_S3HR$secs)
WGSP17_S3HR$secs <- gsub(":", ".", WGSP17_S3HR$secs, perl=TRUE)
WGSP17_S3HR$secs <- stri_sub(WGSP17_S3HR$secs,4)
WGSP17_S3HR$secs <- as.numeric(WGSP17_S3HR$secs)

WGSP17_S3HR <- WGSP17_S3HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.30 & secs<8.30, "WARM_UP",
                     ifelse(secs>11.06 & secs<31.06, "EXERCISE", "BLANK"))))

```

##SESSION 4
```{r}
WGSP17_S4HR <- WGSP17_S4HR%>%
  mutate(session = 4)%>%
  mutate(participant = "P17")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 5.0)%>%
  mutate(type = "SW")
WGSP17_S4HR$session <- as.factor(WGSP17_S4HR$session)
WGSP17_S4HR$secs <- as_hms(WGSP17_S4HR$secs)
WGSP17_S4HR = subset(WGSP17_S4HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP17_S4HR$secs <- as.character(WGSP17_S4HR$secs)
WGSP17_S4HR$secs <- gsub(":", ".", WGSP17_S4HR$secs, perl=TRUE)
WGSP17_S4HR$secs <- stri_sub(WGSP17_S4HR$secs,4)
WGSP17_S4HR$secs <- as.numeric(WGSP17_S4HR$secs)

WGSP17_S4HR <- WGSP17_S4HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.27 & secs<8.27, "WARM_UP",
                     ifelse(secs>8.46 & secs<28.46, "EXERCISE", "BLANK"))))

```

```{r}
WGSP17_HR <- rbind(WGSP17_S1HR, WGSP17_S2HR,WGSP17_S3HR,WGSP17_S4HR)%>%
   mutate(age = 22)%>%
  mutate(sex = "male")%>%
  mutate(HRMAX = (211-(0.64*age)))%>%
  mutate(PerHRMAX = ((hr/HRMAX)*100))
```

#WGSP018
```{r}
WGSP18_S1HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP18//Session1//Parvo//GARMIN_S1.CSV")
WGSP18_S2HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP18//Session2//Parvo//GARMIN_S2.CSV")
WGSP18_S3HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP18//Session3//Parvo//GARMIN_S3.CSV")
WGSP18_S4HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP18//Session4//Parvo//GARMIN_S4.CSV")
```

##SESSION 1
```{r}
WGSP18_S1HR <- WGSP18_S1HR%>%
  mutate(session = 1)%>%
  mutate(participant = "P18")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 130)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 5.9)%>%
  mutate(type = "FWBFR")
WGSP18_S1HR$session <- as.factor(WGSP18_S1HR$session)
WGSP18_S1HR$secs <- as_hms(WGSP18_S1HR$secs)
WGSP18_S1HR = subset(WGSP18_S1HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP18_S1HR$secs <- as.character(WGSP18_S1HR$secs)
WGSP18_S1HR$secs <- gsub(":", ".", WGSP18_S1HR$secs, perl=TRUE)
WGSP18_S1HR$secs <- stri_sub(WGSP18_S1HR$secs,4)
WGSP18_S1HR$secs <- as.numeric(WGSP18_S1HR$secs)

WGSP18_S1HR <- WGSP18_S1HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.39 & secs<8.39, "WARM_UP",
                     ifelse(secs>11.29 & secs<31.29, "EXERCISE", "BLANK"))))

```

##SESSION 2
```{r}
WGSP18_S2HR <- WGSP18_S2HR%>%
  mutate(session = 2)%>%
  mutate(participant = "P18")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 5.9)%>%
  mutate(type = "FW")
WGSP18_S2HR$session <- as.factor(WGSP18_S2HR$session)
WGSP18_S2HR$secs <- as_hms(WGSP18_S2HR$secs)
WGSP18_S2HR = subset(WGSP18_S2HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP18_S2HR$secs <- as.character(WGSP18_S2HR$secs)
WGSP18_S2HR$secs <- gsub(":", ".", WGSP18_S2HR$secs, perl=TRUE)
WGSP18_S2HR$secs <- stri_sub(WGSP18_S2HR$secs,4)
WGSP18_S2HR$secs <- as.numeric(WGSP18_S2HR$secs)

WGSP18_S2HR <- WGSP18_S2HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.28 & secs<8.28, "WARM_UP",
                     ifelse(secs>8.49 & secs<28.49, "EXERCISE", "BLANK"))))

```

##SESSION 3
```{r}
WGSP18_S3HR <- WGSP18_S3HR%>%
  mutate(session = 3)%>%
  mutate(participant = "P18")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 130)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 4.6)%>%
  mutate(type = "SWBFR")
WGSP18_S3HR$session <- as.factor(WGSP18_S3HR$session)
WGSP18_S3HR$secs <- as_hms(WGSP18_S3HR$secs)
WGSP18_S3HR = subset(WGSP18_S3HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP18_S3HR$secs <- as.character(WGSP18_S3HR$secs)
WGSP18_S3HR$secs <- gsub(":", ".", WGSP18_S3HR$secs, perl=TRUE)
WGSP18_S3HR$secs <- stri_sub(WGSP18_S3HR$secs,4)
WGSP18_S3HR$secs <- as.numeric(WGSP18_S3HR$secs)

WGSP18_S3HR <- WGSP18_S3HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>6.20 & secs<9.20, "WARM_UP",
                     ifelse(secs>13.10 & secs<33.30, "EXERCISE", "BLANK"))))

```

##SESSION 4
```{r}
WGSP18_S4HR <- WGSP18_S4HR%>%
  mutate(session = 4)%>%
  mutate(participant = "P18")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 4.6)%>%
  mutate(type = "SW")
WGSP18_S4HR$session <- as.factor(WGSP18_S4HR$session)
WGSP18_S4HR$secs <- as_hms(WGSP18_S4HR$secs)
WGSP18_S4HR = subset(WGSP18_S4HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP18_S4HR$secs <- as.character(WGSP18_S4HR$secs)
WGSP18_S4HR$secs <- gsub(":", ".", WGSP18_S4HR$secs, perl=TRUE)
WGSP18_S4HR$secs <- stri_sub(WGSP18_S4HR$secs,4)
WGSP18_S4HR$secs <- as.numeric(WGSP18_S4HR$secs)

WGSP18_S4HR <- WGSP18_S4HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.26 & secs<8.26, "WARM_UP",
                     ifelse(secs>8.43 & secs<28.43, "EXERCISE", "BLANK"))))

```

```{r}
WGSP18_HR <- rbind(WGSP18_S1HR, WGSP18_S2HR,WGSP18_S3HR,WGSP18_S4HR)%>%
   mutate(age = 23)%>%
  mutate(sex = "male")%>%
  mutate(HRMAX = (211-(0.64*age)))%>%
  mutate(PerHRMAX = ((hr/HRMAX)*100))
```

#WGSP018
```{r}
WGSP19_S1HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP19//Session1//Parvo//GARMIN_S1.CSV")
WGSP19_S2HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP19//Session2//Parvo//GARMIN_S2.CSV")
WGSP19_S3HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP19//Session3//Parvo//GARMIN_S3.CSV")
WGSP19_S4HR <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP19//Session4//Parvo//GARMIN_S4.CSV")
```

##SESSION 1
```{r}
WGSP19_S1HR <- WGSP19_S1HR%>%
  mutate(session = 1)%>%
  mutate(participant = "P19")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 110)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 6.1)%>%
  mutate(type = "FWBFR")
WGSP19_S1HR$session <- as.factor(WGSP19_S1HR$session)
WGSP19_S1HR$secs <- as_hms(WGSP19_S1HR$secs)
WGSP19_S1HR = subset(WGSP19_S1HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP19_S1HR$secs <- as.character(WGSP19_S1HR$secs)
WGSP19_S1HR$secs <- gsub(":", ".", WGSP19_S1HR$secs, perl=TRUE)
WGSP19_S1HR$secs <- stri_sub(WGSP19_S1HR$secs,4)
WGSP19_S1HR$secs <- as.numeric(WGSP19_S1HR$secs)

WGSP19_S1HR <- WGSP19_S1HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>6.03 & secs<9.03, "WARM_UP",
                     ifelse(secs>17.29 & secs<37.29, "EXERCISE", "BLANK"))))

```

##SESSION 2
```{r}
WGSP19_S2HR <- WGSP19_S2HR%>%
  mutate(session = 2)%>%
  mutate(participant = "P19")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 6.1)%>%
  mutate(type = "FW")
WGSP19_S2HR$session <- as.factor(WGSP19_S2HR$session)
WGSP19_S2HR$secs <- as_hms(WGSP19_S2HR$secs)
WGSP19_S2HR = subset(WGSP19_S2HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP19_S2HR$secs <- as.character(WGSP19_S2HR$secs)
WGSP19_S2HR$secs <- gsub(":", ".", WGSP19_S2HR$secs, perl=TRUE)
WGSP19_S2HR$secs <- stri_sub(WGSP19_S2HR$secs,4)
WGSP19_S2HR$secs <- as.numeric(WGSP19_S2HR$secs)

WGSP19_S2HR <- WGSP19_S2HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.40 & secs<8.40, "WARM_UP",
                     ifelse(secs>9.11 & secs<29.11, "EXERCISE", "BLANK"))))

```

##SESSION 3
```{r}
WGSP19_S3HR <- WGSP19_S3HR%>%
  mutate(session = 3)%>%
  mutate(participant = "P19")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 110)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 4.8)%>%
  mutate(type = "SWBFR")
WGSP19_S3HR$session <- as.factor(WGSP19_S3HR$session)
WGSP19_S3HR$secs <- as_hms(WGSP19_S3HR$secs)
WGSP19_S3HR = subset(WGSP19_S3HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP19_S3HR$secs <- as.character(WGSP19_S3HR$secs)
WGSP19_S3HR$secs <- gsub(":", ".", WGSP19_S3HR$secs, perl=TRUE)
WGSP19_S3HR$secs <- stri_sub(WGSP19_S3HR$secs,4)
WGSP19_S3HR$secs <- as.numeric(WGSP19_S3HR$secs)

WGSP19_S3HR <- WGSP19_S3HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>5.34 & secs<8.34, "WARM_UP",
                     ifelse(secs>11.42 & secs<31.42, "EXERCISE", "BLANK"))))

```

##SESSION 4
```{r}
WGSP19_S4HR <- WGSP19_S4HR%>%
  mutate(session = 4)%>%
  mutate(participant = "P19")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 4.8)%>%
  mutate(type = "SW")
WGSP19_S4HR$session <- as.factor(WGSP19_S4HR$session)
WGSP19_S4HR$secs <- as_hms(WGSP19_S4HR$secs)
WGSP19_S4HR = subset(WGSP19_S4HR,select = -c(cad,km,kph,nm,watts,alt,lon,lat,headwind,slope,temp,interval,lrbalance,lte,rte,lps,rps,smo2,thb,o2hb,hhb))
WGSP19_S4HR$secs <- as.character(WGSP19_S4HR$secs)
WGSP19_S4HR$secs <- gsub(":", ".", WGSP19_S4HR$secs, perl=TRUE)
WGSP19_S4HR$secs <- stri_sub(WGSP19_S4HR$secs,4)
WGSP19_S4HR$secs <- as.numeric(WGSP19_S4HR$secs)

WGSP19_S4HR <- WGSP19_S4HR%>%
  mutate(INTERVALS = ifelse(secs>0 & secs<5,"PRE_REST",
                     ifelse(secs>6.07 & secs<9.07, "WARM_UP",
                     ifelse(secs>9.37 & secs<29.37, "EXERCISE", "BLANK"))))

```

```{r}
WGSP19_HR <- rbind(WGSP19_S1HR, WGSP19_S2HR,WGSP19_S3HR,WGSP19_S4HR)%>%
   mutate(age = 22)%>%
  mutate(sex = "female")%>%
  mutate(HRMAX = (211-(0.64*age)))%>%
  mutate(PerHRMAX = ((hr/HRMAX)*100))
```

#Main Data Sheet
```{r}
HRBIND2 <- rbind(WGSP01_HR,WGSP02_HR,WGSP03_HR,WGSP04_HR,WGSP06_HR,WGSP07_HR,WGSP08_HR,WGSP09_HR,WGSP10_HR,WGSP11_HR,WGSP12_HR,WGSP13_HR,WGSP15_HR,WGSP17_HR,WGSP18_HR,WGSP19_HR)
```

```{r}
write.csv(HRBIND,"C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2021\\Study 2 and 3\\AAADATA\\Main CSV sheets\\RAW_HR_DATA(13-12-2021).csv",row.names=FALSE)
```

#Summary
```{r}
HRSUM <- HRBIND%>%
summarySE(measurevar = "hr", groupvar =c("speed","BFR","type","INTERVALS","participant"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)

```
