#Parvo Script
#WGSP01
```{r}
WGSP01_S1PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP01//Session1//Parvo//WGSP01_S1.csv")
WGSP01_S2PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP01//Session2//Parvo//WGSP01_S2.csv")
WGSP01_S3PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP01//Session3//Parvo//WGSP01_S3.csv")
WGSP01_S4PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP01//Session4//Parvo//WGSP01_S4.csv")
```

##Session 1
```{r}
WGSP01_S1PARVOc <- WGSP01_S1PARVO%>%
  mutate(participant = "P1")%>%
  mutate(session = 1)%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 88)%>%
  mutate(speed = "FW")%>%
  mutate(type = "FWBFR")%>%
  mutate(km_h = 6.7)%>%
  mutate(TIME1 = (TIME*60))
  WGSP01_S1PARVOc$TIME1 <- round(WGSP01_S1PARVOc$TIME1, digits = 0)
  WGSP01_S1PARVOc$TIME1 <- as_hms(WGSP01_S1PARVOc$TIME1)
  WGSP01_S1PARVOc$TIME1 <- as.character(WGSP01_S1PARVOc$TIME1)
  WGSP01_S1PARVOc$TIME1 <- gsub(":", ".", WGSP01_S1PARVOc$TIME1, perl=TRUE)
  WGSP01_S1PARVOc$TIME1 <- stri_sub(WGSP01_S1PARVOc$TIME1,4)
  WGSP01_S1PARVOc$TIME1 <- as.numeric(WGSP01_S1PARVOc$TIME1)
  
  WGSP01_S1PARVOc <- WGSP01_S1PARVOc%>%
  mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.45 & TIME1<8.45, "WARM_UP",
                     ifelse(TIME1>12.32 & TIME1<32.32, "EXERCISE", "BLANK"))))
  
```

##Session 2
```{r}
WGSP01_S2PARVOc <- WGSP01_S2PARVO%>%
  mutate(participant = "P1")%>%
  mutate(session = 2)%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "FW")%>%
  mutate(type = "FW")%>%
  mutate(km_h = 6.7)%>%
  mutate(TIME1 = (TIME*60))
  WGSP01_S2PARVOc$TIME1 <- round(WGSP01_S2PARVOc$TIME1, digits = 0)
  WGSP01_S2PARVOc$TIME1 <- as_hms(WGSP01_S2PARVOc$TIME1)
  WGSP01_S2PARVOc$TIME1 <- as.character(WGSP01_S2PARVOc$TIME1)
  WGSP01_S2PARVOc$TIME1 <- gsub(":", ".", WGSP01_S2PARVOc$TIME1, perl=TRUE)
  WGSP01_S2PARVOc$TIME1 <- stri_sub(WGSP01_S2PARVOc$TIME1,4)
  WGSP01_S2PARVOc$TIME1 <- as.numeric(WGSP01_S2PARVOc$TIME1)
  
  WGSP01_S2PARVOc <- WGSP01_S2PARVOc%>%
  mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>6.09 & TIME1<9.09, "WARM_UP",
                     ifelse(TIME1>9.51 & TIME1<29.51, "EXERCISE", "BLANK"))))
```

##Session 3
```{r}
WGSP01_S3PARVOc <- WGSP01_S3PARVO%>%
  mutate(participant = "P1")%>%
  mutate(session = 3)%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 88)%>%
  mutate(speed = "SW")%>%
  mutate(type = "SWBFR")%>%
  mutate(km_h = 5.2)%>%
  mutate(TIME1 = (TIME*60))
  WGSP01_S3PARVOc$TIME1 <- round(WGSP01_S3PARVOc$TIME1, digits = 0)
  WGSP01_S3PARVOc$TIME1 <- as_hms(WGSP01_S3PARVOc$TIME1)
  WGSP01_S3PARVOc$TIME1 <- as.character(WGSP01_S3PARVOc$TIME1)
  WGSP01_S3PARVOc$TIME1 <- gsub(":", ".", WGSP01_S3PARVOc$TIME1, perl=TRUE)
  WGSP01_S3PARVOc$TIME1 <- stri_sub(WGSP01_S3PARVOc$TIME1,4)
  WGSP01_S3PARVOc$TIME1 <- as.numeric(WGSP01_S3PARVOc$TIME1)
  
  WGSP01_S3PARVOc <- WGSP01_S3PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.34 & TIME1<8.34, "WARM_UP",
                     ifelse(TIME1>12.09 & TIME1<32.09, "EXERCISE", "BLANK"))))
```

##Session 4
```{r}
WGSP01_S4PARVOc <- WGSP01_S4PARVO%>%
  mutate(participant = "P1")%>%
  mutate(session = 4)%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "SW")%>%
  mutate(type = "SW")%>%
  mutate(km_h = 5.2)%>%
  mutate(TIME1 = (TIME*60))
  WGSP01_S4PARVOc$TIME1 <- round(WGSP01_S4PARVOc$TIME1, digits = 0)
  WGSP01_S4PARVOc$TIME1 <- as_hms(WGSP01_S4PARVOc$TIME1)
  WGSP01_S4PARVOc$TIME1 <- as.character(WGSP01_S4PARVOc$TIME1)
  WGSP01_S4PARVOc$TIME1 <- gsub(":", ".", WGSP01_S4PARVOc$TIME1, perl=TRUE)
  WGSP01_S4PARVOc$TIME1 <- stri_sub(WGSP01_S4PARVOc$TIME1,4)
  WGSP01_S4PARVOc$TIME1 <- as.numeric(WGSP01_S4PARVOc$TIME1)
  
  WGSP01_S4PARVOc <- WGSP01_S4PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.33 & TIME1<8.33, "WARM_UP",
                     ifelse(TIME1>8.59 & TIME1<28.59, "EXERCISE", "BLANK"))))
```

```{r}
WGSP01_bind <- rbind(WGSP01_S1PARVOc,WGSP01_S2PARVOc,WGSP01_S3PARVOc,WGSP01_S4PARVOc)%>%
  mutate(age = 26)%>%
  mutate(sex = "male")
```

#WGSP02
```{r}
WGSP02_S1PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP02//Session1//Parvo//WGSP02_S1.csv")
WGSP02_S2PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP02//Session2//Parvo//WGSP02_S2.csv")
WGSP02_S3PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP02//Session3//Parvo//WGSP02_S3.csv")
WGSP02_S4PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP02//Session4//Parvo//WGSP02_S4.csv")
```

##Session 1
```{r}
WGSP02_S1PARVOc <- WGSP02_S1PARVO%>%
  mutate(participant = "P2")%>%
  mutate(session = 1)%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 101)%>%
  mutate(speed = "SW")%>%
  mutate(type = "SWBFR")%>%
  mutate(km_h = 5.5)%>%
  mutate(TIME1 = (TIME*60))
  WGSP02_S1PARVOc$TIME1 <- round(WGSP02_S1PARVOc$TIME1, digits = 0)
  WGSP02_S1PARVOc$TIME1 <- as_hms(WGSP02_S1PARVOc$TIME1)
  WGSP02_S1PARVOc$TIME1 <- as.character(WGSP02_S1PARVOc$TIME1)
  WGSP02_S1PARVOc$TIME1 <- gsub(":", ".", WGSP02_S1PARVOc$TIME1, perl=TRUE)
  WGSP02_S1PARVOc$TIME1 <- stri_sub(WGSP02_S1PARVOc$TIME1,4)
  WGSP02_S1PARVOc$TIME1 <- as.numeric(WGSP02_S1PARVOc$TIME1)
  
  WGSP02_S1PARVOc <- WGSP02_S1PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>6.14 & TIME1<9.14, "WARM_UP",
                     ifelse(TIME1>12.27 & TIME1<32.27, "EXERCISE", "BLANK"))))
  
```

##Session 2
```{r}
WGSP02_S2PARVOc <- WGSP02_S2PARVO%>%
  mutate(participant = "P2")%>%
  mutate(session = 2)%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "SW")%>%
  mutate(type = "SW")%>%
  mutate(km_h = 5.5)%>%
  mutate(TIME1 = (TIME*60))
  WGSP02_S2PARVOc$TIME1 <- round(WGSP02_S2PARVOc$TIME1, digits = 0)
  WGSP02_S2PARVOc$TIME1 <- as_hms(WGSP02_S2PARVOc$TIME1)
  WGSP02_S2PARVOc$TIME1 <- as.character(WGSP02_S2PARVOc$TIME1)
  WGSP02_S2PARVOc$TIME1 <- gsub(":", ".", WGSP02_S2PARVOc$TIME1, perl=TRUE)
  WGSP02_S2PARVOc$TIME1 <- stri_sub(WGSP02_S2PARVOc$TIME1,4)
  WGSP02_S2PARVOc$TIME1 <- as.numeric(WGSP02_S2PARVOc$TIME1)
  
  WGSP02_S2PARVOc <- WGSP02_S2PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.29 & TIME1<8.29, "WARM_UP",
                     ifelse(TIME1>8.56 & TIME1<28.56, "EXERCISE", "BLANK"))))

```

##Session 3
```{r}
WGSP02_S3PARVOc <- WGSP02_S3PARVO%>%
  mutate(participant = "P2")%>%
  mutate(session = 3)%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 101)%>%
  mutate(speed = "FW")%>%
  mutate(type = "FWBFR")%>%
  mutate(km_h = 7.1)%>%
  mutate(TIME1 = (TIME*60))
  WGSP02_S3PARVOc$TIME1 <- round(WGSP02_S3PARVOc$TIME1, digits = 0)
  WGSP02_S3PARVOc$TIME1 <- as_hms(WGSP02_S3PARVOc$TIME1)
  WGSP02_S3PARVOc$TIME1 <- as.character(WGSP02_S3PARVOc$TIME1)
  WGSP02_S3PARVOc$TIME1 <- gsub(":", ".", WGSP02_S3PARVOc$TIME1, perl=TRUE)
  WGSP02_S3PARVOc$TIME1 <- stri_sub(WGSP02_S3PARVOc$TIME1,4)
  WGSP02_S3PARVOc$TIME1 <- as.numeric(WGSP02_S3PARVOc$TIME1)
  
  WGSP02_S3PARVOc <- WGSP02_S3PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>6.13 & TIME1<9.13, "WARM_UP",
                     ifelse(TIME1>11.56 & TIME1<31.56, "EXERCISE", "BLANK"))))
```

##Session 4
```{r}
WGSP02_S4PARVOc <- WGSP02_S4PARVO%>%
  mutate(participant = "P2")%>%
  mutate(session = 4)%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "FW")%>%
  mutate(type = "FW")%>%
  mutate(km_h = 7.1)%>%
  mutate(TIME1 = (TIME*60))
  WGSP02_S4PARVOc$TIME1 <- round(WGSP02_S4PARVOc$TIME1, digits = 0)
  WGSP02_S4PARVOc$TIME1 <- as_hms(WGSP02_S4PARVOc$TIME1)
  WGSP02_S4PARVOc$TIME1 <- as.character(WGSP02_S4PARVOc$TIME1)
  WGSP02_S4PARVOc$TIME1 <- gsub(":", ".", WGSP02_S4PARVOc$TIME1, perl=TRUE)
  WGSP02_S4PARVOc$TIME1 <- stri_sub(WGSP02_S4PARVOc$TIME1,4)
  WGSP02_S4PARVOc$TIME1 <- as.numeric(WGSP02_S4PARVOc$TIME1)
  
  WGSP02_S4PARVOc <- WGSP02_S4PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.28 & TIME1<8.28, "WARM_UP",
                     ifelse(TIME1>8.53 & TIME1<28.53, "EXERCISE", "BLANK"))))
```

```{r}
WGSP02_bind <- rbind(WGSP02_S1PARVOc,WGSP02_S2PARVOc,WGSP02_S3PARVOc,WGSP02_S4PARVOc)%>%
  mutate(age = 25)%>%
  mutate(sex = "male")
```

#WGSP03
```{r}
WGSP03_S1PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP03//Session1//Parvo//WGSP03_S1.csv")
WGSP03_S2PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP03//Session2//Parvo//WGSP03_S2.csv")
WGSP03_S3PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP03//Session3//Parvo//WGSP03_S3.csv")
WGSP03_S4PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP03//Session4//Parvo//WGSP03_S4.csv")
```

##Session 1
```{r}
WGSP03_S1PARVOc <- WGSP03_S1PARVO%>%
   mutate(session = 1)%>%
  mutate(participant = "P3")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 90)%>%
  mutate(speed = "FW")%>%
  mutate(type = "FWBFR")%>%
  mutate(km_h = 5.7)%>%
  mutate(TIME1 = (TIME*60))
  WGSP03_S1PARVOc$TIME1 <- round(WGSP03_S1PARVOc$TIME1, digits = 0)
  WGSP03_S1PARVOc$TIME1 <- as_hms(WGSP03_S1PARVOc$TIME1)
  WGSP03_S1PARVOc$TIME1 <- as.character(WGSP03_S1PARVOc$TIME1)
  WGSP03_S1PARVOc$TIME1 <- gsub(":", ".", WGSP03_S1PARVOc$TIME1, perl=TRUE)
  WGSP03_S1PARVOc$TIME1 <- stri_sub(WGSP03_S1PARVOc$TIME1,4)
  WGSP03_S1PARVOc$TIME1 <- as.numeric(WGSP03_S1PARVOc$TIME1)
  
  WGSP03_S1PARVOc <- WGSP03_S1PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.46 & TIME1<8.46, "WARM_UP",
                     ifelse(TIME1>12.49 & TIME1<32.49, "EXERCISE", "BLANK"))))
  
```

##Session 2
```{r}
WGSP03_S2PARVOc <- WGSP03_S2PARVO%>%
  mutate(session = 2)%>%
  mutate(participant = "P3")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "FW")%>%
  mutate(type = "FW")%>%
  mutate(km_h = 5.7)%>%
  mutate(TIME1 = (TIME*60))
  WGSP03_S2PARVOc$TIME1 <- round(WGSP03_S2PARVOc$TIME1, digits = 0)
  WGSP03_S2PARVOc$TIME1 <- as_hms(WGSP03_S2PARVOc$TIME1)
  WGSP03_S2PARVOc$TIME1 <- as.character(WGSP03_S2PARVOc$TIME1)
  WGSP03_S2PARVOc$TIME1 <- gsub(":", ".", WGSP03_S2PARVOc$TIME1, perl=TRUE)
  WGSP03_S2PARVOc$TIME1 <- stri_sub(WGSP03_S2PARVOc$TIME1,4)
  WGSP03_S2PARVOc$TIME1 <- as.numeric(WGSP03_S2PARVOc$TIME1)
  
  WGSP03_S2PARVOc <- WGSP03_S2PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.35 & TIME1<8.35, "WARM_UP",
                     ifelse(TIME1>9.06 & TIME1<29.06, "EXERCISE", "BLANK"))))
    
```

##Session 3
```{r}
WGSP03_S3PARVOc <- WGSP03_S3PARVO%>%
  mutate(session = 3)%>%
  mutate(participant = "P3")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 90)%>%
  mutate(speed = "SW")%>%
  mutate(type = "SWBFR")%>%
  mutate(km_h = 4.4)%>%
  mutate(TIME1 = (TIME*60))
  WGSP03_S3PARVOc$TIME1 <- round(WGSP03_S3PARVOc$TIME1, digits = 0)
  WGSP03_S3PARVOc$TIME1 <- as_hms(WGSP03_S3PARVOc$TIME1)
  WGSP03_S3PARVOc$TIME1 <- as.character(WGSP03_S3PARVOc$TIME1)
  WGSP03_S3PARVOc$TIME1 <- gsub(":", ".", WGSP03_S3PARVOc$TIME1, perl=TRUE)
  WGSP03_S3PARVOc$TIME1 <- stri_sub(WGSP03_S3PARVOc$TIME1,4)
  WGSP03_S3PARVOc$TIME1 <- as.numeric(WGSP03_S3PARVOc$TIME1)
  
  WGSP03_S3PARVOc <- WGSP03_S3PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.34& TIME1<8.34, "WARM_UP",
                     ifelse(TIME1>12.03 & TIME1<32.03, "EXERCISE", "BLANK"))))
```

##Session 4
```{r}
WGSP03_S4PARVOc <- WGSP03_S4PARVO%>%
  mutate(session = 4)%>%
  mutate(participant = "P3")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "SW")%>%
  mutate(type = "SW")%>%
  mutate(km_h = 4.4)%>%
  mutate(TIME1 = (TIME*60))
  WGSP03_S4PARVOc$TIME1 <- round(WGSP03_S4PARVOc$TIME1, digits = 0)
  WGSP03_S4PARVOc$TIME1 <- as_hms(WGSP03_S4PARVOc$TIME1)
  WGSP03_S4PARVOc$TIME1 <- as.character(WGSP03_S4PARVOc$TIME1)
  WGSP03_S4PARVOc$TIME1 <- gsub(":", ".", WGSP03_S4PARVOc$TIME1, perl=TRUE)
  WGSP03_S4PARVOc$TIME1 <- stri_sub(WGSP03_S4PARVOc$TIME1,4)
  WGSP03_S4PARVOc$TIME1 <- as.numeric(WGSP03_S4PARVOc$TIME1)
  
  WGSP03_S4PARVOc <- WGSP03_S4PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.30 & TIME1<8.30, "WARM_UP",
                     ifelse(TIME1>8.50 & TIME1<28.50, "EXERCISE", "BLANK"))))
```

```{r}
WGSP03_bind <- rbind(WGSP03_S1PARVOc,WGSP03_S2PARVOc,WGSP03_S3PARVOc,WGSP03_S4PARVOc)%>%
  mutate(age = 37)%>%
  mutate(sex = "female")
```

#WGSP04
```{r}
WGSP04_S1PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP04//Session1//Parvo//WGSP04_S1.csv")
WGSP04_S2PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP04//Session2//Parvo//WGSP04_S2.csv")
WGSP04_S3PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP04//Session3//Parvo//WGSP04_S3.csv")
WGSP04_S4PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP04//Session4//Parvo//WGSP04_S4.csv")
```

##Session 1
```{r}
WGSP04_S1PARVOc <- WGSP04_S1PARVO%>%
  mutate(participant = "P4")%>%
  mutate(session = 1)%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 102)%>%
  mutate(speed = "SW")%>%
  mutate(type = "SWBFR")%>%
  mutate(km_h = 5.3)%>%
  mutate(TIME1 = (TIME*60))
  WGSP04_S1PARVOc$TIME1 <- round(WGSP04_S1PARVOc$TIME1, digits = 0)
  WGSP04_S1PARVOc$TIME1 <- as_hms(WGSP04_S1PARVOc$TIME1)
  WGSP04_S1PARVOc$TIME1 <- as.character(WGSP04_S1PARVOc$TIME1)
  WGSP04_S1PARVOc$TIME1 <- gsub(":", ".", WGSP04_S1PARVOc$TIME1, perl=TRUE)
  WGSP04_S1PARVOc$TIME1 <- stri_sub(WGSP04_S1PARVOc$TIME1,4)
  WGSP04_S1PARVOc$TIME1 <- as.numeric(WGSP04_S1PARVOc$TIME1)
  
  WGSP04_S1PARVOc <- WGSP04_S1PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>6.09 & TIME1<9.09, "WARM_UP",
                     ifelse(TIME1>12.50 & TIME1<32.50, "EXERCISE", "BLANK"))))
  
```

##Session 2
```{r}
WGSP04_S2PARVOc <- WGSP04_S2PARVO%>%
  mutate(participant = "P4")%>%
  mutate(session = 2)%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "SW")%>%
  mutate(type = "SW")%>%
  mutate(km_h = 5.3)%>%
  mutate(TIME1 = (TIME*60))
  WGSP04_S2PARVOc$TIME1 <- round(WGSP04_S2PARVOc$TIME1, digits = 0)
  WGSP04_S2PARVOc$TIME1 <- as_hms(WGSP04_S2PARVOc$TIME1)
  WGSP04_S2PARVOc$TIME1 <- as.character(WGSP04_S2PARVOc$TIME1)
  WGSP04_S2PARVOc$TIME1 <- gsub(":", ".", WGSP04_S2PARVOc$TIME1, perl=TRUE)
  WGSP04_S2PARVOc$TIME1 <- stri_sub(WGSP04_S2PARVOc$TIME1,4)
  WGSP04_S2PARVOc$TIME1 <- as.numeric(WGSP04_S2PARVOc$TIME1)
  
  WGSP04_S2PARVOc <- WGSP04_S2PARVOc%>%
     mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>6.10 & TIME1<9.10, "WARM_UP",
                     ifelse(TIME1>9.49 & TIME1<27.49, "EXERCISE", "BLANK"))))
    
```

##Session 3
```{r}
WGSP04_S3PARVOc <- WGSP04_S3PARVO%>%
  mutate(participant = "P4")%>%
  mutate(session = 3)%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 102)%>%
  mutate(speed = "FW")%>%
  mutate(type = "FWBFR")%>%
  mutate(km_h = 6.8)%>%
  mutate(TIME1 = (TIME*60))
  WGSP04_S3PARVOc$TIME1 <- round(WGSP04_S3PARVOc$TIME1, digits = 0)
  WGSP04_S3PARVOc$TIME1 <- as_hms(WGSP04_S3PARVOc$TIME1)
  WGSP04_S3PARVOc$TIME1 <- as.character(WGSP04_S3PARVOc$TIME1)
  WGSP04_S3PARVOc$TIME1 <- gsub(":", ".", WGSP04_S3PARVOc$TIME1, perl=TRUE)
  WGSP04_S3PARVOc$TIME1 <- stri_sub(WGSP04_S3PARVOc$TIME1,4)
  WGSP04_S3PARVOc$TIME1 <- as.numeric(WGSP04_S3PARVOc$TIME1)
  
  WGSP04_S3PARVOc <- WGSP04_S3PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.34 & TIME1<8.34, "WARM_UP",
                     ifelse(TIME1>13.02 & TIME1<15.02, "EXERCISE", "BLANK"))))
  
```

##Session 4
```{r}
WGSP04_S4PARVOc <- WGSP04_S4PARVO%>%
  mutate(participant = "P4")%>%
  mutate(session = 4)%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "FW")%>%
  mutate(type = "FW")%>%
  mutate(km_h = 6.8)%>%
  mutate(TIME1 = (TIME*60))
  WGSP04_S4PARVOc$TIME1 <- round(WGSP04_S4PARVOc$TIME1, digits = 0)
  WGSP04_S4PARVOc$TIME1 <- as_hms(WGSP04_S4PARVOc$TIME1)
  WGSP04_S4PARVOc$TIME1 <- as.character(WGSP04_S4PARVOc$TIME1)
  WGSP04_S4PARVOc$TIME1 <- gsub(":", ".", WGSP04_S4PARVOc$TIME1, perl=TRUE)
  WGSP04_S4PARVOc$TIME1 <- stri_sub(WGSP04_S4PARVOc$TIME1,4)
  WGSP04_S4PARVOc$TIME1 <- as.numeric(WGSP04_S4PARVOc$TIME1)
  
  WGSP04_S4PARVOc <- WGSP04_S4PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.42 & TIME1<8.42, "WARM_UP",
                     ifelse(TIME1>9.14 & TIME1<11.14, "EXERCISE", "BLANK"))))
```

```{r}
WGSP04_bind <- rbind(WGSP04_S1PARVOc,WGSP04_S2PARVOc,WGSP04_S3PARVOc,WGSP04_S4PARVOc)%>%
  mutate(age = 29)%>%
  mutate(sex = "female")
```

#WGSP06
```{r}
WGSP06_S1PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP06//Session1//Parvo//WGSP06_S1.csv")
WGSP06_S2PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP06//Session2//Parvo//WGSP06_S2.csv")
WGSP06_S3PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP06//Session3//Parvo//WGSP06_S3.csv")
WGSP06_S4PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP06//Session4//Parvo//WGSP06_S4.csv")
```

##Session 1
```{r}
WGSP06_S1PARVOc <- WGSP06_S1PARVO%>%
  mutate(participant = "P6")%>%
  mutate(session = 1)%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 115)%>%
  mutate(speed = "SW")%>%
  mutate(type = "SWBFR")%>%
  mutate(km_h = 5.3)%>%
  mutate(TIME1 = (TIME*60))
  WGSP06_S1PARVOc$TIME1 <- round(WGSP06_S1PARVOc$TIME1, digits = 0)
  WGSP06_S1PARVOc$TIME1 <- as_hms(WGSP06_S1PARVOc$TIME1)
  WGSP06_S1PARVOc$TIME1 <- as.character(WGSP06_S1PARVOc$TIME1)
  WGSP06_S1PARVOc$TIME1 <- gsub(":", ".", WGSP06_S1PARVOc$TIME1, perl=TRUE)
  WGSP06_S1PARVOc$TIME1 <- stri_sub(WGSP06_S1PARVOc$TIME1,4)
  WGSP06_S1PARVOc$TIME1 <- as.numeric(WGSP06_S1PARVOc$TIME1)
  
  WGSP06_S1PARVOc <- WGSP06_S1PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>6.05 & TIME1<9.05, "WARM_UP",
                     ifelse(TIME1>12.48 & TIME1<32.48, "EXERCISE", "BLANK"))))
  
```

##Session 2
```{r}
WGSP06_S2PARVOc <- WGSP06_S2PARVO%>%
  mutate(participant = "P6")%>%
  mutate(session = 2)%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "SW")%>%
  mutate(type = "SW")%>%
  mutate(km_h = 5.3)%>%
  mutate(TIME1 = (TIME*60))
  WGSP06_S2PARVOc$TIME1 <- round(WGSP06_S2PARVOc$TIME1, digits = 0)
  WGSP06_S2PARVOc$TIME1 <- as_hms(WGSP06_S2PARVOc$TIME1)
  WGSP06_S2PARVOc$TIME1 <- as.character(WGSP06_S2PARVOc$TIME1)
  WGSP06_S2PARVOc$TIME1 <- gsub(":", ".", WGSP06_S2PARVOc$TIME1, perl=TRUE)
  WGSP06_S2PARVOc$TIME1 <- stri_sub(WGSP06_S2PARVOc$TIME1,4)
  WGSP06_S2PARVOc$TIME1 <- as.numeric(WGSP06_S2PARVOc$TIME1)
  
  WGSP06_S2PARVOc <- WGSP06_S2PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>8.10 & TIME1<11.10, "WARM_UP",
                     ifelse(TIME1>11.33 & TIME1<31.33, "EXERCISE", "BLANK"))))
```

##Session 3
```{r}
WGSP06_S3PARVOc <- WGSP06_S3PARVO%>%
  mutate(participant = "P6")%>%
  mutate(session = 3)%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 115)%>%
  mutate(speed = "FW")%>%
  mutate(type = "FWBFR")%>%
  mutate(km_h = 6.8)%>%
  mutate(TIME1 = (TIME*60))
  WGSP06_S3PARVOc$TIME1 <- round(WGSP06_S3PARVOc$TIME1, digits = 0)
  WGSP06_S3PARVOc$TIME1 <- as_hms(WGSP06_S3PARVOc$TIME1)
  WGSP06_S3PARVOc$TIME1 <- as.character(WGSP06_S3PARVOc$TIME1)
  WGSP06_S3PARVOc$TIME1 <- gsub(":", ".", WGSP06_S3PARVOc$TIME1, perl=TRUE)
  WGSP06_S3PARVOc$TIME1 <- stri_sub(WGSP06_S3PARVOc$TIME1,4)
  WGSP06_S3PARVOc$TIME1 <- as.numeric(WGSP06_S3PARVOc$TIME1)
  
  WGSP06_S3PARVOc <- WGSP06_S3PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.50 & TIME1<8.50, "WARM_UP",
                     ifelse(TIME1>13.04 & TIME1<33.04, "EXERCISE", "BLANK"))))
```

##Session 4
```{r}
WGSP06_S4PARVOc <- WGSP06_S4PARVO%>%
  mutate(participant = "P6")%>%
  mutate(session = 4)%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "FW")%>%
  mutate(type = "FW")%>%
  mutate(km_h = 6.8)%>%
  mutate(TIME1 = (TIME*60))
  WGSP06_S4PARVOc$TIME1 <- round(WGSP06_S4PARVOc$TIME1, digits = 0)
  WGSP06_S4PARVOc$TIME1 <- as_hms(WGSP06_S4PARVOc$TIME1)
  WGSP06_S4PARVOc$TIME1 <- as.character(WGSP06_S4PARVOc$TIME1)
  WGSP06_S4PARVOc$TIME1 <- gsub(":", ".", WGSP06_S4PARVOc$TIME1, perl=TRUE)
  WGSP06_S4PARVOc$TIME1 <- stri_sub(WGSP06_S4PARVOc$TIME1,4)
  WGSP06_S4PARVOc$TIME1 <- as.numeric(WGSP06_S4PARVOc$TIME1)
  
  WGSP06_S4PARVOc <- WGSP06_S4PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.56 & TIME1<8.56, "WARM_UP",
                     ifelse(TIME1>9.46 & TIME1<29.46, "EXERCISE", "BLANK"))))
```

```{r}
WGSP06_bind <- rbind(WGSP06_S1PARVOc,WGSP06_S2PARVOc,WGSP06_S3PARVOc,WGSP06_S4PARVOc)%>%
  mutate(age = 30)%>%
  mutate(sex = "male")
```

#WGSP07
```{r}
WGSP07_S1PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP07//Session1//Parvo//WGSP07_S1.csv")
WGSP07_S2PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP07//Session2//Parvo//WGSP07_S2.csv")
WGSP07_S3PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP07//Session3//Parvo//WGSP07_S3.csv")
WGSP07_S4PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP07//Session4//Parvo//WGSP07_S4.csv")
```

##Session 1
```{r}
WGSP07_S1PARVOc <- WGSP07_S1PARVO%>%
  mutate(participant = "P7")%>%
  mutate(session = 1)%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 102)%>%
  mutate(speed = "SW")%>%
  mutate(type = "SWBFR")%>%
  mutate(km_h = 4.9)%>%
  mutate(TIME1 = (TIME*60))
  WGSP07_S1PARVOc$TIME1 <- round(WGSP07_S1PARVOc$TIME1, digits = 0)
  WGSP07_S1PARVOc$TIME1 <- as_hms(WGSP07_S1PARVOc$TIME1)
  WGSP07_S1PARVOc$TIME1 <- as.character(WGSP07_S1PARVOc$TIME1)
  WGSP07_S1PARVOc$TIME1 <- gsub(":", ".", WGSP07_S1PARVOc$TIME1, perl=TRUE)
  WGSP07_S1PARVOc$TIME1 <- stri_sub(WGSP07_S1PARVOc$TIME1,4)
  WGSP07_S1PARVOc$TIME1 <- as.numeric(WGSP07_S1PARVOc$TIME1)
  
  WGSP07_S1PARVOc <- WGSP07_S1PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>6.23 & TIME1<9.23, "WARM_UP",
                     ifelse(TIME1>12.50 & TIME1<32.50, "EXERCISE", "BLANK"))))
  
```

##Session 2
```{r}
WGSP07_S2PARVOc <- WGSP07_S2PARVO%>%
  mutate(participant = "P7")%>%
  mutate(session = 2)%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "SW")%>%
  mutate(type = "SW")%>%
  mutate(km_h = 4.9)%>%
  mutate(TIME1 = (TIME*60))
  WGSP07_S2PARVOc$TIME1 <- round(WGSP07_S2PARVOc$TIME1, digits = 0)
  WGSP07_S2PARVOc$TIME1 <- as_hms(WGSP07_S2PARVOc$TIME1)
  WGSP07_S2PARVOc$TIME1 <- as.character(WGSP07_S2PARVOc$TIME1)
  WGSP07_S2PARVOc$TIME1 <- gsub(":", ".", WGSP07_S2PARVOc$TIME1, perl=TRUE)
  WGSP07_S2PARVOc$TIME1 <- stri_sub(WGSP07_S2PARVOc$TIME1,4)
  WGSP07_S2PARVOc$TIME1 <- as.numeric(WGSP07_S2PARVOc$TIME1)
  
  WGSP07_S2PARVOc <- WGSP07_S2PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.30 & TIME1<8.30, "WARM_UP",
                     ifelse(TIME1>9.10 & TIME1<29.10, "EXERCISE", "BLANK"))))
```

##Session 3
```{r}
WGSP07_S3PARVOc <- WGSP07_S3PARVO%>%
  mutate(participant = "P7")%>%
  mutate(session = 3)%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 102)%>%
  mutate(speed = "FW")%>%
  mutate(type = "FWBFR")%>%
  mutate(km_h = 6.3)%>%
  mutate(TIME1 = (TIME*60))
  WGSP07_S3PARVOc$TIME1 <- round(WGSP07_S3PARVOc$TIME1, digits = 0)
  WGSP07_S3PARVOc$TIME1 <- as_hms(WGSP07_S3PARVOc$TIME1)
  WGSP07_S3PARVOc$TIME1 <- as.character(WGSP07_S3PARVOc$TIME1)
  WGSP07_S3PARVOc$TIME1 <- gsub(":", ".", WGSP07_S3PARVOc$TIME1, perl=TRUE)
  WGSP07_S3PARVOc$TIME1 <- stri_sub(WGSP07_S3PARVOc$TIME1,4)
  WGSP07_S3PARVOc$TIME1 <- as.numeric(WGSP07_S3PARVOc$TIME1)
  
  WGSP07_S3PARVOc <- WGSP07_S3PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.47 & TIME1<8.47, "WARM_UP",
                     ifelse(TIME1>11.39 & TIME1<31.39, "EXERCISE", "BLANK"))))
  
```

##Session 4
```{r}
WGSP07_S4PARVOc <- WGSP07_S4PARVO%>%
  mutate(participant = "P7")%>%
  mutate(session = 4)%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "FW")%>%
  mutate(type = "FW")%>%
  mutate(km_h = 6.3)%>%
  mutate(TIME1 = (TIME*60))
  WGSP07_S4PARVOc$TIME1 <- round(WGSP07_S4PARVOc$TIME1, digits = 0)
  WGSP07_S4PARVOc$TIME1 <- as_hms(WGSP07_S4PARVOc$TIME1)
  WGSP07_S4PARVOc$TIME1 <- as.character(WGSP07_S4PARVOc$TIME1)
  WGSP07_S4PARVOc$TIME1 <- gsub(":", ".", WGSP07_S4PARVOc$TIME1, perl=TRUE)
  WGSP07_S4PARVOc$TIME1 <- stri_sub(WGSP07_S4PARVOc$TIME1,4)
  WGSP07_S4PARVOc$TIME1 <- as.numeric(WGSP07_S4PARVOc$TIME1)
  
  WGSP07_S4PARVOc <- WGSP07_S4PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.50 & TIME1<8.50, "WARM_UP",
                     ifelse(TIME1>9.22 & TIME1<29.22, "EXERCISE", "BLANK"))))
```

```{r}
WGSP07_bind <- rbind(WGSP07_S1PARVOc,WGSP07_S2PARVOc,WGSP07_S3PARVOc,WGSP07_S4PARVOc)%>%
  mutate(age = 23)%>%
  mutate(sex = "male")
```

#WGSP08
```{r}
WGSP08_S1PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP08//Session1//Parvo//WGSP08_S1.csv")
WGSP08_S2PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP08//Session2//Parvo//WGSP08_S2.csv")
WGSP08_S3PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP08//Session3//Parvo//WGSP08_S3.csv")
WGSP08_S4PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP08//Session4//Parvo//WGSP08_S4.csv")
```

##Session 1
```{r}
WGSP08_S1PARVOc <- WGSP08_S1PARVO%>%
  mutate(participant = "P8")%>%
  mutate(session = 1)%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 116)%>%
  mutate(speed = "SW")%>%
  mutate(type = "SWBFR")%>%
  mutate(km_h = 5.2)%>%
  mutate(TIME1 = (TIME*60))
  WGSP08_S1PARVOc$TIME1 <- round(WGSP08_S1PARVOc$TIME1, digits = 0)
  WGSP08_S1PARVOc$TIME1 <- as_hms(WGSP08_S1PARVOc$TIME1)
  WGSP08_S1PARVOc$TIME1 <- as.character(WGSP08_S1PARVOc$TIME1)
  WGSP08_S1PARVOc$TIME1 <- gsub(":", ".", WGSP08_S1PARVOc$TIME1, perl=TRUE)
  WGSP08_S1PARVOc$TIME1 <- stri_sub(WGSP08_S1PARVOc$TIME1,4)
  WGSP08_S1PARVOc$TIME1 <- as.numeric(WGSP08_S1PARVOc$TIME1)
  
  WGSP08_S1PARVOc <- WGSP08_S1PARVOc%>%
  mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>13.38 & TIME1<16.38, "WARM_UP",
                     ifelse(TIME1>19.47 & TIME1<39.47, "EXERCISE", "BLANK"))))
```

##Session 2
```{r}
WGSP08_S2PARVOc <- WGSP08_S2PARVO%>%
  mutate(participant = "P8")%>%
  mutate(session = 2)%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "SW")%>%
  mutate(type = "SW")%>%
  mutate(km_h = 5.2)%>%
  mutate(TIME1 = (TIME*60))
  WGSP08_S2PARVOc$TIME1 <- round(WGSP08_S2PARVOc$TIME1, digits = 0)
  WGSP08_S2PARVOc$TIME1 <- as_hms(WGSP08_S2PARVOc$TIME1)
  WGSP08_S2PARVOc$TIME1 <- as.character(WGSP08_S2PARVOc$TIME1)
  WGSP08_S2PARVOc$TIME1 <- gsub(":", ".", WGSP08_S2PARVOc$TIME1, perl=TRUE)
  WGSP08_S2PARVOc$TIME1 <- stri_sub(WGSP08_S2PARVOc$TIME1,4)
  WGSP08_S2PARVOc$TIME1 <- as.numeric(WGSP08_S2PARVOc$TIME1)
  
  WGSP08_S2PARVOc <- WGSP08_S2PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.35 & TIME1<8.35, "WARM_UP",
                     ifelse(TIME1>9.04 & TIME1<29.04, "EXERCISE", "BLANK"))))
```

##Session 3
```{r}
WGSP08_S3PARVOc <- WGSP08_S3PARVO%>%
  mutate(participant = "P8")%>%
  mutate(session = 3)%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 116)%>%
  mutate(speed = "FW")%>%
  mutate(type = "FWBFR")%>%
  mutate(km_h = 6.7)%>%
  mutate(TIME1 = (TIME*60))
  WGSP08_S3PARVOc$TIME1 <- round(WGSP08_S3PARVOc$TIME1, digits = 0)
  WGSP08_S3PARVOc$TIME1 <- as_hms(WGSP08_S3PARVOc$TIME1)
  WGSP08_S3PARVOc$TIME1 <- as.character(WGSP08_S3PARVOc$TIME1)
  WGSP08_S3PARVOc$TIME1 <- gsub(":", ".", WGSP08_S3PARVOc$TIME1, perl=TRUE)
  WGSP08_S3PARVOc$TIME1 <- stri_sub(WGSP08_S3PARVOc$TIME1,4)
  WGSP08_S3PARVOc$TIME1 <- as.numeric(WGSP08_S3PARVOc$TIME1)
  
  WGSP08_S3PARVOc <- WGSP08_S3PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.28 & TIME1<8.28, "WARM_UP",
                     ifelse(TIME1>12.24 & TIME1<17.24, "EXERCISE", "BLANK"))))
```

##Session 4
```{r}
WGSP08_S4PARVOc <- WGSP08_S4PARVO%>%
  mutate(participant = "P8")%>%
  mutate(session = 4)%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "FW")%>%
  mutate(type = "FW")%>%
  mutate(km_h = 6.7)%>%
  mutate(TIME1 = (TIME*60))
  WGSP08_S4PARVOc$TIME1 <- round(WGSP08_S4PARVOc$TIME1, digits = 0)
  WGSP08_S4PARVOc$TIME1 <- as_hms(WGSP08_S4PARVOc$TIME1)
  WGSP08_S4PARVOc$TIME1 <- as.character(WGSP08_S4PARVOc$TIME1)
  WGSP08_S4PARVOc$TIME1 <- gsub(":", ".", WGSP08_S4PARVOc$TIME1, perl=TRUE)
  WGSP08_S4PARVOc$TIME1 <- stri_sub(WGSP08_S4PARVOc$TIME1,4)
  WGSP08_S4PARVOc$TIME1 <- as.numeric(WGSP08_S4PARVOc$TIME1)
  
  WGSP08_S4PARVOc <- WGSP08_S4PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.33 & TIME1<8.33, "WARM_UP",
                     ifelse(TIME1>8.59 & TIME1<13.59, "EXERCISE", "BLANK"))))
```

```{r}
WGSP08_bind <- rbind(WGSP08_S1PARVOc,WGSP08_S2PARVOc,WGSP08_S3PARVOc,WGSP08_S4PARVOc)%>%
  mutate(age = 22)%>%
  mutate(sex = "female")
```

#WGSP09
```{r}
WGSP09_S1PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP09//Session1//Parvo//WGSP09_S1.csv")
WGSP09_S2PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP09//Session2//Parvo//WGSP09_S2.csv")
WGSP09_S3PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP09//Session3//Parvo//WGSP09_S3.csv")
WGSP09_S4PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP09//Session4//Parvo//WGSP09_S4.csv")
```

##Session 1
```{r}
WGSP09_S1PARVOc <- WGSP09_S1PARVO%>%
  mutate(participant = "P9")%>%
  mutate(session = 1)%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 108)%>%
  mutate(speed = "FW")%>%
  mutate(type = "FWBFR")%>%
  mutate(km_h = 7.0)%>%
  mutate(TIME1 = (TIME*60))
  WGSP09_S1PARVOc$TIME1 <- round(WGSP09_S1PARVOc$TIME1, digits = 0)
  WGSP09_S1PARVOc$TIME1 <- as_hms(WGSP09_S1PARVOc$TIME1)
  WGSP09_S1PARVOc$TIME1 <- as.character(WGSP09_S1PARVOc$TIME1)
  WGSP09_S1PARVOc$TIME1 <- gsub(":", ".", WGSP09_S1PARVOc$TIME1, perl=TRUE)
  WGSP09_S1PARVOc$TIME1 <- stri_sub(WGSP09_S1PARVOc$TIME1,4)
  WGSP09_S1PARVOc$TIME1 <- as.numeric(WGSP09_S1PARVOc$TIME1)
  
  WGSP09_S1PARVOc <- WGSP09_S1PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>6.05 & TIME1<9.05, "WARM_UP",
                     ifelse(TIME1>12.16 & TIME1<18.08, "EXERCISE", "BLANK"))))
  
```

##Session 2
```{r}
WGSP09_S2PARVOc <- WGSP09_S2PARVO%>%
  mutate(participant = "P9")%>%
  mutate(session = 2)%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "FW")%>%
  mutate(type = "FW")%>%
  mutate(km_h = 7.0)%>%
  mutate(TIME1 = (TIME*60))
  WGSP09_S2PARVOc$TIME1 <- round(WGSP09_S2PARVOc$TIME1, digits = 0)
  WGSP09_S2PARVOc$TIME1 <- as_hms(WGSP09_S2PARVOc$TIME1)
  WGSP09_S2PARVOc$TIME1 <- as.character(WGSP09_S2PARVOc$TIME1)
  WGSP09_S2PARVOc$TIME1 <- gsub(":", ".", WGSP09_S2PARVOc$TIME1, perl=TRUE)
  WGSP09_S2PARVOc$TIME1 <- stri_sub(WGSP09_S2PARVOc$TIME1,4)
  WGSP09_S2PARVOc$TIME1 <- as.numeric(WGSP09_S2PARVOc$TIME1)
  
  WGSP09_S2PARVOc <- WGSP09_S2PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.30 & TIME1<8.30, "WARM_UP",
                     ifelse(TIME1>8.56 & TIME1<14.56, "EXERCISE", "BLANK"))))
```

##Session 3
```{r}
WGSP09_S3PARVOc <- WGSP09_S3PARVO%>%
  mutate(participant = "P9")%>%
  mutate(session = 3)%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 108)%>%
  mutate(speed = "SW")%>%
  mutate(type = "SWBFR")%>%
  mutate(km_h = 5.5)%>%
  mutate(TIME1 = (TIME*60))
  WGSP09_S3PARVOc$TIME1 <- round(WGSP09_S3PARVOc$TIME1, digits = 0)
  WGSP09_S3PARVOc$TIME1 <- as_hms(WGSP09_S3PARVOc$TIME1)
  WGSP09_S3PARVOc$TIME1 <- as.character(WGSP09_S3PARVOc$TIME1)
  WGSP09_S3PARVOc$TIME1 <- gsub(":", ".", WGSP09_S3PARVOc$TIME1, perl=TRUE)
  WGSP09_S3PARVOc$TIME1 <- stri_sub(WGSP09_S3PARVOc$TIME1,4)
  WGSP09_S3PARVOc$TIME1 <- as.numeric(WGSP09_S3PARVOc$TIME1)
  
  WGSP09_S3PARVOc <- WGSP09_S3PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.34 & TIME1<8.34, "WARM_UP",
                     ifelse(TIME1>11.43 & TIME1<31.43, "EXERCISE", "BLANK"))))
```

##Session 4
```{r}
WGSP09_S4PARVOc <- WGSP09_S4PARVO%>%
  mutate(participant = "P9")%>%
  mutate(session = 4)%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "SW")%>%
  mutate(type = "SW")%>%
  mutate(km_h = 5.5)%>%
  mutate(TIME1 = (TIME*60))
  WGSP09_S4PARVOc$TIME1 <- round(WGSP09_S4PARVOc$TIME1, digits = 0)
  WGSP09_S4PARVOc$TIME1 <- as_hms(WGSP09_S4PARVOc$TIME1)
  WGSP09_S4PARVOc$TIME1 <- as.character(WGSP09_S4PARVOc$TIME1)
  WGSP09_S4PARVOc$TIME1 <- gsub(":", ".", WGSP09_S4PARVOc$TIME1, perl=TRUE)
  WGSP09_S4PARVOc$TIME1 <- stri_sub(WGSP09_S4PARVOc$TIME1,4)
  WGSP09_S4PARVOc$TIME1 <- as.numeric(WGSP09_S4PARVOc$TIME1)
  
  WGSP09_S4PARVOc <- WGSP09_S4PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.30 & TIME1<8.30, "WARM_UP",
                     ifelse(TIME1>9.08 & TIME1<29.08, "EXERCISE", "BLANK"))))
```

```{r}
WGSP09_bind <- rbind(WGSP09_S1PARVOc,WGSP09_S2PARVOc,WGSP09_S3PARVOc,WGSP09_S4PARVOc)%>%
  mutate(age = 29)%>%
  mutate(sex = "male")
```

#WGSP10
```{r}
WGSP10_S1PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP10//Session1//Parvo//WGSP10_S1.csv")
WGSP10_S2PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP10//Session2//Parvo//WGSP10_S2.csv")
WGSP10_S3PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP10//Session3//Parvo//WGSP10_S3.csv")
WGSP10_S4PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP10//Session4//Parvo//WGSP10_S4.csv")
```

##Session 1
```{r}
WGSP10_S1PARVOc <- WGSP10_S1PARVO%>%
  mutate(session = 1)%>%
  mutate(participant = "P10")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 185)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 5.3)%>%
  mutate(type = "SWBFR")%>%
  mutate(TIME1 = (TIME*60))
  WGSP10_S1PARVOc$TIME1 <- round(WGSP10_S1PARVOc$TIME1, digits = 0)
  WGSP10_S1PARVOc$TIME1 <- as_hms(WGSP10_S1PARVOc$TIME1)
  WGSP10_S1PARVOc$TIME1 <- as.character(WGSP10_S1PARVOc$TIME1)
  WGSP10_S1PARVOc$TIME1 <- gsub(":", ".", WGSP10_S1PARVOc$TIME1, perl=TRUE)
  WGSP10_S1PARVOc$TIME1 <- stri_sub(WGSP10_S1PARVOc$TIME1,4)
  WGSP10_S1PARVOc$TIME1 <- as.numeric(WGSP10_S1PARVOc$TIME1)
  
  WGSP10_S1PARVOc <- WGSP10_S1PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.41 & TIME1<8.41, "WARM_UP",
                     ifelse(TIME1>11.28 & TIME1<31.28, "EXERCISE", "BLANK"))))
  
```

##Session 2
```{r}
WGSP10_S2PARVOc <- WGSP10_S2PARVO%>%
  mutate(session = 2)%>%
  mutate(participant = "P10")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 5.3)%>%
  mutate(type = "SW")%>%
  mutate(TIME1 = (TIME*60))
  WGSP10_S2PARVOc$TIME1 <- round(WGSP10_S2PARVOc$TIME1, digits = 0)
  WGSP10_S2PARVOc$TIME1 <- as_hms(WGSP10_S2PARVOc$TIME1)
  WGSP10_S2PARVOc$TIME1 <- as.character(WGSP10_S2PARVOc$TIME1)
  WGSP10_S2PARVOc$TIME1 <- gsub(":", ".", WGSP10_S2PARVOc$TIME1, perl=TRUE)
  WGSP10_S2PARVOc$TIME1 <- stri_sub(WGSP10_S2PARVOc$TIME1,4)
  WGSP10_S2PARVOc$TIME1 <- as.numeric(WGSP10_S2PARVOc$TIME1)
  
  WGSP10_S2PARVOc <- WGSP10_S2PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0.10 & TIME1<5.10,"PRE_REST",
                     ifelse(TIME1>6.41 & TIME1<9.41, "WARM_UP",
                     ifelse(TIME1>10.17 & TIME1<30.17, "EXERCISE", "BLANK"))))
```

##Session 3
```{r}
WGSP10_S3PARVOc <- WGSP10_S3PARVO%>%
  mutate(session = 3)%>%
  mutate(participant = "P10")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 85)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 6.8)%>%
  mutate(type = "FWBFR")%>%
  mutate(TIME1 = (TIME*60))
  WGSP10_S3PARVOc$TIME1 <- round(WGSP10_S3PARVOc$TIME1, digits = 0)
  WGSP10_S3PARVOc$TIME1 <- as_hms(WGSP10_S3PARVOc$TIME1)
  WGSP10_S3PARVOc$TIME1 <- as.character(WGSP10_S3PARVOc$TIME1)
  WGSP10_S3PARVOc$TIME1 <- gsub(":", ".", WGSP10_S3PARVOc$TIME1, perl=TRUE)
  WGSP10_S3PARVOc$TIME1 <- stri_sub(WGSP10_S3PARVOc$TIME1,4)
  WGSP10_S3PARVOc$TIME1 <- as.numeric(WGSP10_S3PARVOc$TIME1)
  
  WGSP10_S3PARVOc <- WGSP10_S3PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.28 & TIME1<8.28, "WARM_UP",
                     ifelse(TIME1>11.20 & TIME1<31.20, "EXERCISE", "BLANK"))))
```

##Session 4
```{r}
WGSP10_S4PARVOc <- WGSP10_S4PARVO%>%
  mutate(session = 4)%>%
  mutate(participant = "P10")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 6.8)%>%
  mutate(type = "FW")%>%
  mutate(TIME1 = (TIME*60))
  WGSP10_S4PARVOc$TIME1 <- round(WGSP10_S4PARVOc$TIME1, digits = 0)
  WGSP10_S4PARVOc$TIME1 <- as_hms(WGSP10_S4PARVOc$TIME1)
  WGSP10_S4PARVOc$TIME1 <- as.character(WGSP10_S4PARVOc$TIME1)
  WGSP10_S4PARVOc$TIME1 <- gsub(":", ".", WGSP10_S4PARVOc$TIME1, perl=TRUE)
  WGSP10_S4PARVOc$TIME1 <- stri_sub(WGSP10_S4PARVOc$TIME1,4)
  WGSP10_S4PARVOc$TIME1 <- as.numeric(WGSP10_S4PARVOc$TIME1)
  
  WGSP10_S4PARVOc <- WGSP10_S4PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.37 & TIME1<8.37, "WARM_UP",
                     ifelse(TIME1>9.03 & TIME1<29.03, "EXERCISE", "BLANK"))))
```

```{r}
WGSP10_bind <- rbind(WGSP10_S1PARVOc,WGSP10_S2PARVOc,WGSP10_S3PARVOc,WGSP10_S4PARVOc)%>%
  mutate(age = 29)%>%
  mutate(sex = "male")
```
#WGSP11
```{r}
WGSP11_S1PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP11//Session1//Parvo//WGSP011_S1.csv")
WGSP11_S2PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP11//Session2//Parvo//WGSP011_S2.csv")
WGSP11_S3PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP11//Session3//Parvo//WGSP011_S3.csv")
WGSP11_S4PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP11//Session4//Parvo//WGSP011_S4.csv")
```

##Session 1
```{r}
WGSP11_S1PARVOc <- WGSP11_S1PARVO%>%
  mutate(participant = "P11")%>%
  mutate(session = 1)%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 94)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 4.6)%>%
  mutate(type = "SWBFR")%>%
  mutate(TIME1 = (TIME*60))
  WGSP11_S1PARVOc$TIME1 <- round(WGSP11_S1PARVOc$TIME1, digits = 0)
  WGSP11_S1PARVOc$TIME1 <- as_hms(WGSP11_S1PARVOc$TIME1)
  WGSP11_S1PARVOc$TIME1 <- as.character(WGSP11_S1PARVOc$TIME1)
  WGSP11_S1PARVOc$TIME1 <- gsub(":", ".", WGSP11_S1PARVOc$TIME1, perl=TRUE)
  WGSP11_S1PARVOc$TIME1 <- stri_sub(WGSP11_S1PARVOc$TIME1,4)
  WGSP11_S1PARVOc$TIME1 <- as.numeric(WGSP11_S1PARVOc$TIME1)
  
  WGSP11_S1PARVOc <- WGSP11_S1PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.33 & TIME1<8.33, "WARM_UP",
                     ifelse(TIME1>11.24 & TIME1<20.24, "EXERCISE", "BLANK"))))
  
```

##Session 2
```{r}
WGSP11_S2PARVOc <- WGSP11_S2PARVO%>%
  mutate(participant = "P11")%>%
  mutate(session = 2)%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 94)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 5.9)%>%
  mutate(type = "FWBFR")%>%
  mutate(TIME1 = (TIME*60))
  WGSP11_S2PARVOc$TIME1 <- round(WGSP11_S2PARVOc$TIME1, digits = 0)
  WGSP11_S2PARVOc$TIME1 <- as_hms(WGSP11_S2PARVOc$TIME1)
  WGSP11_S2PARVOc$TIME1 <- as.character(WGSP11_S2PARVOc$TIME1)
  WGSP11_S2PARVOc$TIME1 <- gsub(":", ".", WGSP11_S2PARVOc$TIME1, perl=TRUE)
  WGSP11_S2PARVOc$TIME1 <- stri_sub(WGSP11_S2PARVOc$TIME1,4)
  WGSP11_S2PARVOc$TIME1 <- as.numeric(WGSP11_S2PARVOc$TIME1)
  
  WGSP11_S2PARVOc <- WGSP11_S2PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.45 & TIME1<8.45, "WARM_UP",
                     ifelse(TIME1>12.01 & TIME1<19.08, "EXERCISE", "BLANK"))))
```

##Session 3
```{r}
WGSP11_S3PARVOc <- WGSP11_S3PARVO%>%
  mutate(participant = "P11")%>%
  mutate(session = 3)%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 4.6)%>%
  mutate(type = "SW")%>%
  mutate(TIME1 = (TIME*60))
  WGSP11_S3PARVOc$TIME1 <- round(WGSP11_S3PARVOc$TIME1, digits = 0)
  WGSP11_S3PARVOc$TIME1 <- as_hms(WGSP11_S3PARVOc$TIME1)
  WGSP11_S3PARVOc$TIME1 <- as.character(WGSP11_S3PARVOc$TIME1)
  WGSP11_S3PARVOc$TIME1 <- gsub(":", ".", WGSP11_S3PARVOc$TIME1, perl=TRUE)
  WGSP11_S3PARVOc$TIME1 <- stri_sub(WGSP11_S3PARVOc$TIME1,4)
  WGSP11_S3PARVOc$TIME1 <- as.numeric(WGSP11_S3PARVOc$TIME1)
  
  WGSP11_S3PARVOc <- WGSP11_S3PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.35 & TIME1<8.35, "WARM_UP",
                     ifelse(TIME1>9.00 & TIME1<18.00, "EXERCISE", "BLANK"))))
```

##Session 4
```{r}
WGSP11_S4PARVOc <- WGSP11_S4PARVO%>%
  mutate(participant = "P11")%>%
  mutate(session = 4)%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 4.9)%>%
  mutate(type = "FW")%>%
  mutate(TIME1 = (TIME*60))
  WGSP11_S4PARVOc$TIME1 <- round(WGSP11_S4PARVOc$TIME1, digits = 0)
  WGSP11_S4PARVOc$TIME1 <- as_hms(WGSP11_S4PARVOc$TIME1)
  WGSP11_S4PARVOc$TIME1 <- as.character(WGSP11_S4PARVOc$TIME1)
  WGSP11_S4PARVOc$TIME1 <- gsub(":", ".", WGSP11_S4PARVOc$TIME1, perl=TRUE)
  WGSP11_S4PARVOc$TIME1 <- stri_sub(WGSP11_S4PARVOc$TIME1,4)
  WGSP11_S4PARVOc$TIME1 <- as.numeric(WGSP11_S4PARVOc$TIME1)
  
  WGSP11_S4PARVOc <- WGSP11_S4PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.30 & TIME1<8.30, "WARM_UP",
                     ifelse(TIME1>9.19 & TIME1<16.19, "EXERCISE", "BLANK"))))
```

```{r}
WGSP11_bind <- rbind(WGSP11_S1PARVOc,WGSP11_S2PARVOc,WGSP11_S3PARVOc,WGSP11_S4PARVOc)%>%
  mutate(age = 31)%>%
  mutate(sex = "male")
```

#WGSP12
```{r}
WGSP12_S1PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP12//Session1//Parvo//WGSP012_S1.csv")
WGSP12_S2PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP12//Session2//Parvo//WGSP012_S2.csv")
WGSP12_S3PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP12//Session3//Parvo//WGSP012_S3.csv")
WGSP12_S4PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP12//Session4//Parvo//WGSP012_S4.csv")
```

##Session 1
```{r}
WGSP12_S1PARVOc <- WGSP12_S1PARVO%>%
  mutate(participant = "P12")%>%
  mutate(session = 1)%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 104)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 6.1)%>%
  mutate(type = "FWBFR")%>%
  mutate(TIME1 = (TIME*60))
  WGSP12_S1PARVOc$TIME1 <- round(WGSP12_S1PARVOc$TIME1, digits = 0)
  WGSP12_S1PARVOc$TIME1 <- as_hms(WGSP12_S1PARVOc$TIME1)
  WGSP12_S1PARVOc$TIME1 <- as.character(WGSP12_S1PARVOc$TIME1)
  WGSP12_S1PARVOc$TIME1 <- gsub(":", ".", WGSP12_S1PARVOc$TIME1, perl=TRUE)
  WGSP12_S1PARVOc$TIME1 <- stri_sub(WGSP12_S1PARVOc$TIME1,4)
  WGSP12_S1PARVOc$TIME1 <- as.numeric(WGSP12_S1PARVOc$TIME1)
  
  WGSP12_S1PARVOc <- WGSP12_S1PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>6.04 & TIME1<9.04, "WARM_UP",
                     ifelse(TIME1>13.32 & TIME1<33.32, "EXERCISE", "BLANK"))))
  
```

##Session 2
```{r}
WGSP12_S2PARVOc <- WGSP12_S2PARVO%>%
  mutate(participant = "P12")%>%
  mutate(session = 2)%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 6.1)%>%
  mutate(type = "FW")%>%
  mutate(TIME1 = (TIME*60))
  WGSP12_S2PARVOc$TIME1 <- round(WGSP12_S2PARVOc$TIME1, digits = 0)
  WGSP12_S2PARVOc$TIME1 <- as_hms(WGSP12_S2PARVOc$TIME1)
  WGSP12_S2PARVOc$TIME1 <- as.character(WGSP12_S2PARVOc$TIME1)
  WGSP12_S2PARVOc$TIME1 <- gsub(":", ".", WGSP12_S2PARVOc$TIME1, perl=TRUE)
  WGSP12_S2PARVOc$TIME1 <- stri_sub(WGSP12_S2PARVOc$TIME1,4)
  WGSP12_S2PARVOc$TIME1 <- as.numeric(WGSP12_S2PARVOc$TIME1)
  
  WGSP12_S2PARVOc <- WGSP12_S2PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.35 & TIME1<8.35, "WARM_UP",
                     ifelse(TIME1>9.01 & TIME1<29.01, "EXERCISE", "BLANK"))))
```

##Session 3
```{r}
WGSP12_S3PARVOc <- WGSP12_S3PARVO%>%
  mutate(participant = "P12")%>%
  mutate(session = 3)%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 104)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 4.8)%>%
  mutate(type = "SWBFR")%>%
  mutate(TIME1 = (TIME*60))
  WGSP12_S3PARVOc$TIME1 <- round(WGSP12_S3PARVOc$TIME1, digits = 0)
  WGSP12_S3PARVOc$TIME1 <- as_hms(WGSP12_S3PARVOc$TIME1)
  WGSP12_S3PARVOc$TIME1 <- as.character(WGSP12_S3PARVOc$TIME1)
  WGSP12_S3PARVOc$TIME1 <- gsub(":", ".", WGSP12_S3PARVOc$TIME1, perl=TRUE)
  WGSP12_S3PARVOc$TIME1 <- stri_sub(WGSP12_S3PARVOc$TIME1,4)
  WGSP12_S3PARVOc$TIME1 <- as.numeric(WGSP12_S3PARVOc$TIME1)
  
  WGSP12_S3PARVOc <- WGSP12_S3PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.44 & TIME1<8.44, "WARM_UP",
                     ifelse(TIME1>11.25 & TIME1<19.25, "EXERCISE", "BLANK"))))
```

##Session 4
```{r}
WGSP12_S4PARVOc <- WGSP12_S4PARVO%>%
  mutate(participant = "P12")%>%
  mutate(session = 4)%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 4.8)%>%
  mutate(type = "SW")%>%
  mutate(TIME1 = (TIME*60))
  WGSP12_S4PARVOc$TIME1 <- round(WGSP12_S4PARVOc$TIME1, digits = 0)
  WGSP12_S4PARVOc$TIME1 <- as_hms(WGSP12_S4PARVOc$TIME1)
  WGSP12_S4PARVOc$TIME1 <- as.character(WGSP12_S4PARVOc$TIME1)
  WGSP12_S4PARVOc$TIME1 <- gsub(":", ".", WGSP12_S4PARVOc$TIME1, perl=TRUE)
  WGSP12_S4PARVOc$TIME1 <- stri_sub(WGSP12_S4PARVOc$TIME1,4)
  WGSP12_S4PARVOc$TIME1 <- as.numeric(WGSP12_S4PARVOc$TIME1)
  
  WGSP12_S4PARVOc <- WGSP12_S4PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.34 & TIME1<8.34, "WARM_UP",
                     ifelse(TIME1>8.55 & TIME1<16.55, "EXERCISE", "BLANK"))))
```

```{r}
WGSP12_bind <- rbind(WGSP12_S1PARVOc,WGSP12_S2PARVOc,WGSP12_S3PARVOc,WGSP12_S4PARVOc)%>%
  mutate(age = 23)%>%
  mutate(sex = "male")
```

#WGSP13
```{r}
WGSP13_S1PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP13//Session1//Parvo//WGSP013_S1.csv")
WGSP13_S2PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP13//Session2//Parvo//WGSP013_S2.csv")
WGSP13_S3PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP13//Session3//Parvo//WGSP013_S3.csv")
WGSP13_S4PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP13//Session4//Parvo//WGSP013_S4.csv")
```

##Session 1
```{r}
WGSP13_S1PARVOc <- WGSP13_S1PARVO%>%
  mutate(session = 1)%>%
  mutate(participant = "P13")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 96)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 5.1)%>%
  mutate(type = "SWBFR")%>%
  mutate(TIME1 = (TIME*60))
  WGSP13_S1PARVOc$TIME1 <- round(WGSP13_S1PARVOc$TIME1, digits = 0)
  WGSP13_S1PARVOc$TIME1 <- as_hms(WGSP13_S1PARVOc$TIME1)
  WGSP13_S1PARVOc$TIME1 <- as.character(WGSP13_S1PARVOc$TIME1)
  WGSP13_S1PARVOc$TIME1 <- gsub(":", ".", WGSP13_S1PARVOc$TIME1, perl=TRUE)
  WGSP13_S1PARVOc$TIME1 <- stri_sub(WGSP13_S1PARVOc$TIME1,4)
  WGSP13_S1PARVOc$TIME1 <- as.numeric(WGSP13_S1PARVOc$TIME1)
  
  WGSP13_S1PARVOc <- WGSP13_S1PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.33 & TIME1<8.33, "WARM_UP",
                     ifelse(TIME1>11.33 & TIME1<31.33, "EXERCISE", "BLANK"))))
  
```

##Session 2
```{r}
WGSP13_S2PARVOc <- WGSP13_S2PARVO%>%
  mutate(session = 2)%>%
  mutate(participant = "P13")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 5.1)%>%
  mutate(type = "SW")%>%
  mutate(TIME1 = (TIME*60))
  WGSP13_S2PARVOc$TIME1 <- round(WGSP13_S2PARVOc$TIME1, digits = 0)
  WGSP13_S2PARVOc$TIME1 <- as_hms(WGSP13_S2PARVOc$TIME1)
  WGSP13_S2PARVOc$TIME1 <- as.character(WGSP13_S2PARVOc$TIME1)
  WGSP13_S2PARVOc$TIME1 <- gsub(":", ".", WGSP13_S2PARVOc$TIME1, perl=TRUE)
  WGSP13_S2PARVOc$TIME1 <- stri_sub(WGSP13_S2PARVOc$TIME1,4)
  WGSP13_S2PARVOc$TIME1 <- as.numeric(WGSP13_S2PARVOc$TIME1)
  
  WGSP13_S2PARVOc <- WGSP13_S2PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.34 & TIME1<8.34, "WARM_UP",
                     ifelse(TIME1>8.56 & TIME1<28.56, "EXERCISE", "BLANK"))))
```

##Session 3
```{r}
WGSP13_S3PARVOc <- WGSP13_S3PARVO%>%
  mutate(session = 3)%>%
  mutate(participant = "P13")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 96)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 6.6)%>%
  mutate(type = "FWBFR")%>%
  mutate(TIME1 = (TIME*60))
  WGSP13_S3PARVOc$TIME1 <- round(WGSP13_S3PARVOc$TIME1, digits = 0)
  WGSP13_S3PARVOc$TIME1 <- as_hms(WGSP13_S3PARVOc$TIME1)
  WGSP13_S3PARVOc$TIME1 <- as.character(WGSP13_S3PARVOc$TIME1)
  WGSP13_S3PARVOc$TIME1 <- gsub(":", ".", WGSP13_S3PARVOc$TIME1, perl=TRUE)
  WGSP13_S3PARVOc$TIME1 <- stri_sub(WGSP13_S3PARVOc$TIME1,4)
  WGSP13_S3PARVOc$TIME1 <- as.numeric(WGSP13_S3PARVOc$TIME1)
  
  WGSP13_S3PARVOc <- WGSP13_S3PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.25 & TIME1<8.25, "WARM_UP",
                     ifelse(TIME1>11.30 & TIME1<31.30, "EXERCISE", "BLANK"))))
```

##Session 4
```{r}
WGSP13_S4PARVOc <- WGSP13_S4PARVO%>%
  mutate(session = 4)%>%
  mutate(participant = "P13")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 6.6)%>%
  mutate(type = "FW")%>%
  mutate(TIME1 = (TIME*60))
  WGSP13_S4PARVOc$TIME1 <- round(WGSP13_S4PARVOc$TIME1, digits = 0)
  WGSP13_S4PARVOc$TIME1 <- as_hms(WGSP13_S4PARVOc$TIME1)
  WGSP13_S4PARVOc$TIME1 <- as.character(WGSP13_S4PARVOc$TIME1)
  WGSP13_S4PARVOc$TIME1 <- gsub(":", ".", WGSP13_S4PARVOc$TIME1, perl=TRUE)
  WGSP13_S4PARVOc$TIME1 <- stri_sub(WGSP13_S4PARVOc$TIME1,4)
  WGSP13_S4PARVOc$TIME1 <- as.numeric(WGSP13_S4PARVOc$TIME1)
  
  WGSP13_S4PARVOc <- WGSP13_S4PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.42 & TIME1<8.42, "WARM_UP",
                     ifelse(TIME1>9.53 & TIME1<29.53, "EXERCISE", "BLANK"))))
```

```{r}
WGSP13_bind <- rbind(WGSP13_S1PARVOc,WGSP13_S2PARVOc,WGSP13_S3PARVOc,WGSP13_S4PARVOc)%>%
  mutate(age = 32)%>%
  mutate(sex = "male")
```

#WGSP15
```{r}
WGSP15_S1PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP15//Session1//Parvo//WGSP015_S1.csv")
WGSP15_S2PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP15//Session2//Parvo//WGSP015_S2.csv")
WGSP15_S3PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP15//Session3//Parvo//WGSP015_S3.csv")
WGSP15_S4PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP15//Session4//Parvo//WGSP015_S4.csv")
```

##Session 1
```{r}
WGSP15_S1PARVOc <- WGSP15_S1PARVO%>%
  mutate(session = 1)%>%
  mutate(participant = "P15")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 114)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 6.3)%>%
  mutate(type = "FWBFR")%>%
  mutate(TIME1 = (TIME*60))
  WGSP15_S1PARVOc$TIME1 <- round(WGSP15_S1PARVOc$TIME1, digits = 0)
  WGSP15_S1PARVOc$TIME1 <- as_hms(WGSP15_S1PARVOc$TIME1)
  WGSP15_S1PARVOc$TIME1 <- as.character(WGSP15_S1PARVOc$TIME1)
  WGSP15_S1PARVOc$TIME1 <- gsub(":", ".", WGSP15_S1PARVOc$TIME1, perl=TRUE)
  WGSP15_S1PARVOc$TIME1 <- stri_sub(WGSP15_S1PARVOc$TIME1,4)
  WGSP15_S1PARVOc$TIME1 <- as.numeric(WGSP15_S1PARVOc$TIME1)
  
  WGSP15_S1PARVOc <- WGSP15_S1PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.32 & TIME1<8.32, "WARM_UP",
                     ifelse(TIME1>11.37 & TIME1<24.37, "EXERCISE", "BLANK"))))
```

##Session 2
```{r}
WGSP15_S2PARVOc <- WGSP15_S2PARVO%>%
  mutate(session = 2)%>%
  mutate(participant = "P15")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 6.3)%>%
  mutate(type = "FW")%>%
  mutate(TIME1 = (TIME*60))
  WGSP15_S2PARVOc$TIME1 <- round(WGSP15_S2PARVOc$TIME1, digits = 0)
  WGSP15_S2PARVOc$TIME1 <- as_hms(WGSP15_S2PARVOc$TIME1)
  WGSP15_S2PARVOc$TIME1 <- as.character(WGSP15_S2PARVOc$TIME1)
  WGSP15_S2PARVOc$TIME1 <- gsub(":", ".", WGSP15_S2PARVOc$TIME1, perl=TRUE)
  WGSP15_S2PARVOc$TIME1 <- stri_sub(WGSP15_S2PARVOc$TIME1,4)
  WGSP15_S2PARVOc$TIME1 <- as.numeric(WGSP15_S2PARVOc$TIME1)
  
  WGSP15_S2PARVOc <- WGSP15_S2PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.32 & TIME1<8.32, "WARM_UP",
                     ifelse(TIME1>8.59 & TIME1<21.59, "EXERCISE", "BLANK"))))
```

##Session 3
```{r}
WGSP15_S3PARVOc <- WGSP15_S3PARVO%>%
  mutate(session = 3)%>%
  mutate(participant = "P15")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 114)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 4.9)%>%
  mutate(type = "SWBFR")%>%
  mutate(TIME1 = (TIME*60))
  WGSP15_S3PARVOc$TIME1 <- round(WGSP15_S3PARVOc$TIME1, digits = 0)
  WGSP15_S3PARVOc$TIME1 <- as_hms(WGSP15_S3PARVOc$TIME1)
  WGSP15_S3PARVOc$TIME1 <- as.character(WGSP15_S3PARVOc$TIME1)
  WGSP15_S3PARVOc$TIME1 <- gsub(":", ".", WGSP15_S3PARVOc$TIME1, perl=TRUE)
  WGSP15_S3PARVOc$TIME1 <- stri_sub(WGSP15_S3PARVOc$TIME1,4)
  WGSP15_S3PARVOc$TIME1 <- as.numeric(WGSP15_S3PARVOc$TIME1)
  
  WGSP15_S3PARVOc <- WGSP15_S3PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.27 & TIME1<8.27, "WARM_UP",
                     ifelse(TIME1>11.00 & TIME1<31.00, "EXERCISE", "BLANK"))))
```

##Session 4
```{r}
WGSP15_S4PARVOc <- WGSP15_S4PARVO%>%
  mutate(session = 4)%>%
  mutate(participant = "P15")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 4.9)%>%
  mutate(type = "SW")%>%
  mutate(TIME1 = (TIME*60))
  WGSP15_S4PARVOc$TIME1 <- round(WGSP15_S4PARVOc$TIME1, digits = 0)
  WGSP15_S4PARVOc$TIME1 <- as_hms(WGSP15_S4PARVOc$TIME1)
  WGSP15_S4PARVOc$TIME1 <- as.character(WGSP15_S4PARVOc$TIME1)
  WGSP15_S4PARVOc$TIME1 <- gsub(":", ".", WGSP15_S4PARVOc$TIME1, perl=TRUE)
  WGSP15_S4PARVOc$TIME1 <- stri_sub(WGSP15_S4PARVOc$TIME1,4)
  WGSP15_S4PARVOc$TIME1 <- as.numeric(WGSP15_S4PARVOc$TIME1)
  
  WGSP15_S4PARVOc <- WGSP15_S4PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.54 & TIME1<8.54, "WARM_UP",
                     ifelse(TIME1>9.38 & TIME1<29.38, "EXERCISE", "BLANK"))))
```

```{r}
WGSP15_bind <- rbind(WGSP15_S1PARVOc,WGSP15_S2PARVOc,WGSP15_S3PARVOc,WGSP15_S4PARVOc)%>%
  mutate(age = 29)%>%
  mutate(sex = "male")
```

#WGSP17
```{r}
WGSP17_S1PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP17//Session1//Parvo//WGSP017_S1.csv")
WGSP17_S2PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP17//Session2//Parvo//WGSP017_S2.csv")
WGSP17_S3PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP17//Session3//Parvo//WGSP017_S3.csv")
WGSP17_S4PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP17//Session4//Parvo//WGSP017_S4.csv")
```

##Session 1
```{r}
WGSP17_S1PARVOc <- WGSP17_S1PARVO%>%
  mutate(session = 1)%>%
  mutate(participant = "P17")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 100)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 6.5)%>%
  mutate(type = "FWBFR")%>%
  mutate(TIME1 = (TIME*60))
  WGSP17_S1PARVOc$TIME1 <- round(WGSP17_S1PARVOc$TIME1, digits = 0)
  WGSP17_S1PARVOc$TIME1 <- as_hms(WGSP17_S1PARVOc$TIME1)
  WGSP17_S1PARVOc$TIME1 <- as.character(WGSP17_S1PARVOc$TIME1)
  WGSP17_S1PARVOc$TIME1 <- gsub(":", ".", WGSP17_S1PARVOc$TIME1, perl=TRUE)
  WGSP17_S1PARVOc$TIME1 <- stri_sub(WGSP17_S1PARVOc$TIME1,4)
  WGSP17_S1PARVOc$TIME1 <- as.numeric(WGSP17_S1PARVOc$TIME1)
  
  WGSP17_S1PARVOc <- WGSP17_S1PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.32 & TIME1<8.32, "WARM_UP",
                     ifelse(TIME1>11.37 & TIME1<24.37, "EXERCISE", "BLANK"))))
```

##Session 2
```{r}
WGSP17_S2PARVOc <- WGSP17_S2PARVO%>%
  mutate(session = 2)%>%
  mutate(participant = "P17")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 6.5)%>%
  mutate(type = "FW")%>%
  mutate(TIME1 = (TIME*60))
  WGSP17_S2PARVOc$TIME1 <- round(WGSP17_S2PARVOc$TIME1, digits = 0)
  WGSP17_S2PARVOc$TIME1 <- as_hms(WGSP17_S2PARVOc$TIME1)
  WGSP17_S2PARVOc$TIME1 <- as.character(WGSP17_S2PARVOc$TIME1)
  WGSP17_S2PARVOc$TIME1 <- gsub(":", ".", WGSP17_S2PARVOc$TIME1, perl=TRUE)
  WGSP17_S2PARVOc$TIME1 <- stri_sub(WGSP17_S2PARVOc$TIME1,4)
  WGSP17_S2PARVOc$TIME1 <- as.numeric(WGSP17_S2PARVOc$TIME1)
  
  WGSP17_S2PARVOc <- WGSP17_S2PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.32 & TIME1<8.32, "WARM_UP",
                     ifelse(TIME1>8.59 & TIME1<21.59, "EXERCISE", "BLANK"))))
```

##Session 3
```{r}
WGSP17_S3PARVOc <- WGSP17_S3PARVO%>%
  mutate(session = 3)%>%
  mutate(participant = "P17")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 100)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 5.0)%>%
  mutate(type = "SWBFR")%>%
  mutate(TIME1 = (TIME*60))
  WGSP17_S3PARVOc$TIME1 <- round(WGSP17_S3PARVOc$TIME1, digits = 0)
  WGSP17_S3PARVOc$TIME1 <- as_hms(WGSP17_S3PARVOc$TIME1)
  WGSP17_S3PARVOc$TIME1 <- as.character(WGSP17_S3PARVOc$TIME1)
  WGSP17_S3PARVOc$TIME1 <- gsub(":", ".", WGSP17_S3PARVOc$TIME1, perl=TRUE)
  WGSP17_S3PARVOc$TIME1 <- stri_sub(WGSP17_S3PARVOc$TIME1,4)
  WGSP17_S3PARVOc$TIME1 <- as.numeric(WGSP17_S3PARVOc$TIME1)
  
  WGSP17_S3PARVOc <- WGSP17_S3PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.27 & TIME1<8.27, "WARM_UP",
                     ifelse(TIME1>11.00 & TIME1<31.00, "EXERCISE", "BLANK"))))
```

##Session 4
```{r}
WGSP17_S4PARVOc <- WGSP17_S4PARVO%>%
  mutate(session = 4)%>%
  mutate(participant = "P17")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 5.0)%>%
  mutate(type = "SW")%>%
  mutate(TIME1 = (TIME*60))
  WGSP17_S4PARVOc$TIME1 <- round(WGSP17_S4PARVOc$TIME1, digits = 0)
  WGSP17_S4PARVOc$TIME1 <- as_hms(WGSP17_S4PARVOc$TIME1)
  WGSP17_S4PARVOc$TIME1 <- as.character(WGSP17_S4PARVOc$TIME1)
  WGSP17_S4PARVOc$TIME1 <- gsub(":", ".", WGSP17_S4PARVOc$TIME1, perl=TRUE)
  WGSP17_S4PARVOc$TIME1 <- stri_sub(WGSP17_S4PARVOc$TIME1,4)
  WGSP17_S4PARVOc$TIME1 <- as.numeric(WGSP17_S4PARVOc$TIME1)
  
  WGSP17_S4PARVOc <- WGSP17_S4PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.54 & TIME1<8.54, "WARM_UP",
                     ifelse(TIME1>9.38 & TIME1<29.38, "EXERCISE", "BLANK"))))
```

```{r}
WGSP17_bind <- rbind(WGSP17_S1PARVOc,WGSP17_S2PARVOc,WGSP17_S3PARVOc,WGSP17_S4PARVOc)%>%
  mutate(age = 22)%>%
  mutate(sex = "male")
```

#WGSP18
```{r}
WGSP18_S1PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP18//Session1//Parvo//WGSP018_S1.csv")
WGSP18_S2PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP18//Session2//Parvo//WGSP018_S2.csv")
WGSP18_S3PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP18//Session3//Parvo//WGSP018_S3.csv")
WGSP18_S4PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP18//Session4//Parvo//WGSP018_S4.csv")
```

##Session 1
```{r}
WGSP18_S1PARVOc <- WGSP18_S1PARVO%>%
  mutate(session = 1)%>%
  mutate(participant = "P18")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 130)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 5.9)%>%
  mutate(type = "FWBFR")%>%
  mutate(TIME1 = (TIME*60))
  WGSP18_S1PARVOc$TIME1 <- round(WGSP18_S1PARVOc$TIME1, digits = 0)
  WGSP18_S1PARVOc$TIME1 <- as_hms(WGSP18_S1PARVOc$TIME1)
  WGSP18_S1PARVOc$TIME1 <- as.character(WGSP18_S1PARVOc$TIME1)
  WGSP18_S1PARVOc$TIME1 <- gsub(":", ".", WGSP18_S1PARVOc$TIME1, perl=TRUE)
  WGSP18_S1PARVOc$TIME1 <- stri_sub(WGSP18_S1PARVOc$TIME1,4)
  WGSP18_S1PARVOc$TIME1 <- as.numeric(WGSP18_S1PARVOc$TIME1)
  
  WGSP18_S1PARVOc <- WGSP18_S1PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.39 & TIME1<8.39, "WARM_UP",
                     ifelse(TIME1>11.29 & TIME1<31.29, "EXERCISE", "BLANK"))))
  
```

##Session 2
```{r}
WGSP18_S2PARVOc <- WGSP18_S2PARVO%>%
  mutate(session = 2)%>%
  mutate(participant = "P18")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 5.9)%>%
  mutate(type = "FW")%>%
  mutate(TIME1 = (TIME*60))
  WGSP18_S2PARVOc$TIME1 <- round(WGSP18_S2PARVOc$TIME1, digits = 0)
  WGSP18_S2PARVOc$TIME1 <- as_hms(WGSP18_S2PARVOc$TIME1)
  WGSP18_S2PARVOc$TIME1 <- as.character(WGSP18_S2PARVOc$TIME1)
  WGSP18_S2PARVOc$TIME1 <- gsub(":", ".", WGSP18_S2PARVOc$TIME1, perl=TRUE)
  WGSP18_S2PARVOc$TIME1 <- stri_sub(WGSP18_S2PARVOc$TIME1,4)
  WGSP18_S2PARVOc$TIME1 <- as.numeric(WGSP18_S2PARVOc$TIME1)
  
  WGSP18_S2PARVOc <- WGSP18_S2PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.28 & TIME1<8.28, "WARM_UP",
                     ifelse(TIME1>8.49 & TIME1<28.49, "EXERCISE", "BLANK"))))
```

##Session 3
```{r}
WGSP18_S3PARVOc <- WGSP18_S3PARVO%>%
  mutate(session = 3)%>%
  mutate(participant = "P18")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 130)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 4.6)%>%
  mutate(type = "SWBFR")%>%
  mutate(TIME1 = (TIME*60))
  WGSP18_S3PARVOc$TIME1 <- round(WGSP18_S3PARVOc$TIME1, digits = 0)
  WGSP18_S3PARVOc$TIME1 <- as_hms(WGSP18_S3PARVOc$TIME1)
  WGSP18_S3PARVOc$TIME1 <- as.character(WGSP18_S3PARVOc$TIME1)
  WGSP18_S3PARVOc$TIME1 <- gsub(":", ".", WGSP18_S3PARVOc$TIME1, perl=TRUE)
  WGSP18_S3PARVOc$TIME1 <- stri_sub(WGSP18_S3PARVOc$TIME1,4)
  WGSP18_S3PARVOc$TIME1 <- as.numeric(WGSP18_S3PARVOc$TIME1)
  
  WGSP18_S3PARVOc <- WGSP18_S3PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>6.20 & TIME1<9.20, "WARM_UP",
                     ifelse(TIME1>13.10 & TIME1<33.30, "EXERCISE", "BLANK"))))
```

##Session 4
```{r}
WGSP18_S4PARVOc <- WGSP18_S4PARVO%>%
  mutate(session = 4)%>%
  mutate(participant = "P18")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 4.6)%>%
  mutate(type = "SW")%>%
  mutate(TIME1 = (TIME*60))
  WGSP18_S4PARVOc$TIME1 <- round(WGSP18_S4PARVOc$TIME1, digits = 0)
  WGSP18_S4PARVOc$TIME1 <- as_hms(WGSP18_S4PARVOc$TIME1)
  WGSP18_S4PARVOc$TIME1 <- as.character(WGSP18_S4PARVOc$TIME1)
  WGSP18_S4PARVOc$TIME1 <- gsub(":", ".", WGSP18_S4PARVOc$TIME1, perl=TRUE)
  WGSP18_S4PARVOc$TIME1 <- stri_sub(WGSP18_S4PARVOc$TIME1,4)
  WGSP18_S4PARVOc$TIME1 <- as.numeric(WGSP18_S4PARVOc$TIME1)
  
  WGSP18_S4PARVOc <- WGSP18_S4PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.26 & TIME1<8.26, "WARM_UP",
                     ifelse(TIME1>8.43 & TIME1<28.43, "EXERCISE", "BLANK"))))
```

```{r}
WGSP18_bind <- rbind(WGSP18_S1PARVOc,WGSP18_S2PARVOc,WGSP18_S3PARVOc,WGSP18_S4PARVOc)%>%
  mutate(age = 23)%>%
  mutate(sex = "male")
```

#WGSP19
```{r}
WGSP19_S1PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP19//Session1//Parvo//WGSP019_S1.csv")
WGSP19_S2PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP19//Session2//Parvo//WGSP019_S2.csv")
WGSP19_S3PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP19//Session3//Parvo//WGSP019_S3.csv")
WGSP19_S4PARVO <- read.csv("C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2021//Study 2 and 3//AAADATA//Participants//WGSP19//Session4//Parvo//WGSP019_S4.csv")
```

##Session 1
```{r}
WGSP19_S1PARVOc <- WGSP19_S1PARVO%>%
  mutate(session = 1)%>%
  mutate(participant = "P19")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 110)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 6.1)%>%
  mutate(type = "FWBFR")%>%
  mutate(TIME1 = (TIME*60))
  WGSP19_S1PARVOc$TIME1 <- round(WGSP19_S1PARVOc$TIME1, digits = 0)
  WGSP19_S1PARVOc$TIME1 <- as_hms(WGSP19_S1PARVOc$TIME1)
  WGSP19_S1PARVOc$TIME1 <- as.character(WGSP19_S1PARVOc$TIME1)
  WGSP19_S1PARVOc$TIME1 <- gsub(":", ".", WGSP19_S1PARVOc$TIME1, perl=TRUE)
  WGSP19_S1PARVOc$TIME1 <- stri_sub(WGSP19_S1PARVOc$TIME1,4)
  WGSP19_S1PARVOc$TIME1 <- as.numeric(WGSP19_S1PARVOc$TIME1)
  
  WGSP19_S1PARVOc <- WGSP19_S1PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.39 & TIME1<8.39, "WARM_UP",
                     ifelse(TIME1>11.29 & TIME1<31.29, "EXERCISE", "BLANK"))))
  
```

##Session 2
```{r}
WGSP19_S2PARVOc <- WGSP19_S2PARVO%>%
  mutate(session = 2)%>%
  mutate(participant = "P19")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "FW")%>%
  mutate(km_h = 6.1)%>%
  mutate(type = "FW")%>%
  mutate(TIME1 = (TIME*60))
  WGSP19_S2PARVOc$TIME1 <- round(WGSP19_S2PARVOc$TIME1, digits = 0)
  WGSP19_S2PARVOc$TIME1 <- as_hms(WGSP19_S2PARVOc$TIME1)
  WGSP19_S2PARVOc$TIME1 <- as.character(WGSP19_S2PARVOc$TIME1)
  WGSP19_S2PARVOc$TIME1 <- gsub(":", ".", WGSP19_S2PARVOc$TIME1, perl=TRUE)
  WGSP19_S2PARVOc$TIME1 <- stri_sub(WGSP19_S2PARVOc$TIME1,4)
  WGSP19_S2PARVOc$TIME1 <- as.numeric(WGSP19_S2PARVOc$TIME1)
  
  WGSP19_S2PARVOc <- WGSP19_S2PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.28 & TIME1<8.28, "WARM_UP",
                     ifelse(TIME1>8.49 & TIME1<28.49, "EXERCISE", "BLANK"))))
```

##Session 3
```{r}
WGSP19_S3PARVOc <- WGSP19_S3PARVO%>%
  mutate(session = 3)%>%
  mutate(participant = "P19")%>%
  mutate(BFR = "YES")%>%
  mutate(AOP = 110)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 4.8)%>%
  mutate(type = "SWBFR")%>%
  mutate(TIME1 = (TIME*60))
  WGSP19_S3PARVOc$TIME1 <- round(WGSP19_S3PARVOc$TIME1, digits = 0)
  WGSP19_S3PARVOc$TIME1 <- as_hms(WGSP19_S3PARVOc$TIME1)
  WGSP19_S3PARVOc$TIME1 <- as.character(WGSP19_S3PARVOc$TIME1)
  WGSP19_S3PARVOc$TIME1 <- gsub(":", ".", WGSP19_S3PARVOc$TIME1, perl=TRUE)
  WGSP19_S3PARVOc$TIME1 <- stri_sub(WGSP19_S3PARVOc$TIME1,4)
  WGSP19_S3PARVOc$TIME1 <- as.numeric(WGSP19_S3PARVOc$TIME1)
  
  WGSP19_S3PARVOc <- WGSP19_S3PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>6.20 & TIME1<9.20, "WARM_UP",
                     ifelse(TIME1>13.10 & TIME1<33.30, "EXERCISE", "BLANK"))))
```

##Session 4
```{r}
WGSP19_S4PARVOc <- WGSP19_S4PARVO%>%
  mutate(session = 4)%>%
  mutate(participant = "P19")%>%
  mutate(BFR = "NO")%>%
  mutate(AOP = 0)%>%
  mutate(speed = "SW")%>%
  mutate(km_h = 4.8)%>%
  mutate(type = "SW")%>%
  mutate(TIME1 = (TIME*60))
  WGSP19_S4PARVOc$TIME1 <- round(WGSP19_S4PARVOc$TIME1, digits = 0)
  WGSP19_S4PARVOc$TIME1 <- as_hms(WGSP19_S4PARVOc$TIME1)
  WGSP19_S4PARVOc$TIME1 <- as.character(WGSP19_S4PARVOc$TIME1)
  WGSP19_S4PARVOc$TIME1 <- gsub(":", ".", WGSP19_S4PARVOc$TIME1, perl=TRUE)
  WGSP19_S4PARVOc$TIME1 <- stri_sub(WGSP19_S4PARVOc$TIME1,4)
  WGSP19_S4PARVOc$TIME1 <- as.numeric(WGSP19_S4PARVOc$TIME1)
  
  WGSP19_S4PARVOc <- WGSP19_S4PARVOc%>%
    mutate(INTERVALS = ifelse(TIME1>0 & TIME1<5,"PRE_REST",
                     ifelse(TIME1>5.26 & TIME1<8.26, "WARM_UP",
                     ifelse(TIME1>8.43 & TIME1<28.43, "EXERCISE", "BLANK"))))
```

```{r}
WGSP19_bind <- rbind(WGSP19_S1PARVOc,WGSP19_S2PARVOc,WGSP19_S3PARVOc,WGSP19_S4PARVOc)%>%
  mutate(age = 22)%>%
  mutate(sex = "female")
```
#Study Bind
```{r}
Study2PARVOBIND <- rbind(WGSP01_bind,WGSP02_bind,WGSP03_bind,WGSP04_bind,WGSP06_bind,WGSP07_bind,WGSP08_bind,WGSP09_bind,WGSP11_bind,WGSP12_bind,WGSP13_bind,WGSP15_bind,WGSP18_bind)
```

```{r}
write.csv(Study2PARVOBIND,"C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2021\\Study 2 and 3\\AAADATA\\Main CSV sheets\\RAW_PARVO_DATA(13-12-2021).csv",row.names=FALSE)
```

#Summary
```{r}
VESUM <- Study2PARVOBIND%>%
summarySE(measurevar = "VE", groupvar =c("speed","BFR","participant"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)

FECO2SUM <- Study2PARVOBIND%>%
summarySE(measurevar = "FECO2", groupvar =c("INTERVALS", "BFR"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)%>%
  filter(!INTERVALS %in% "BLANK")
```

